---
title: "POEM TX Paper 2 (APCD Data) - Mental Health"
date: today
format: 
  docx:
    df-print: paged
    page-layout: full
    fig-width: 12
    fig-height: 8
    out-width: 100%
  html:
    fig-width: 12
    fig-height: 8
editor: source
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r setup}
#| echo: false
#| warning: false

# Load packages 
pacman::p_load(RPostgres, DBI, keyring, janitor, tidyverse, readxl,
               gtsummary, ggplot2, labelled, clipr, viridis, ggrepel, scales, ggthemes, flextable,
               odbc, openxlsx, beepr, tictoc, here, lubridate, patchwork, cowplot)

#### Setup File Paths ####
current_dir <- here::here()

#### Database Connection 
greenplum_user = "jwozny"

apcd <- dbConnect(RPostgres::Postgres(),
                 dbname = "apcd_dev",
                 user = "jwozny",
                 password = key_get("apcd_dev", greenplum_user),
                 host = "spgpcdplv001",
                 bigint = "integer")

options(scipen = 999)

# Set Themes
my_theme <- function() {
  theme_minimal(base_size = 10) +
    theme(
      text = element_text(family = "sans", size=14),
      axis.text.y = element_text(size = 12, face="plain", margin = margin(r = 10, unit = "pt")),
      axis.title.y = element_text(size = 13, face = "bold", margin = margin(r = 20, unit = "pt")),
      axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 20, unit = "pt")),
      plot.caption = element_text(size = 12, face = "italic", margin = margin(t = 20, r=20, b = 5, l=20, unit = "pt"))
    )
}

set_flextable_defaults(padding=2.5)
theme_set(my_theme())

FitFlextableToPage <- function(ft, pgwidth = 6.5){
  ft_out <- ft %>% autofit()
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}
```

```{r get-data}

all.df <- dbGetQuery(apcd, "
  select * from research_dev.poem_cohort_analysis2
;")

# Replace NAs
all.df[sapply(all.df, is.numeric)] <- 
  lapply(all.df[sapply(all.df, is.numeric)], function(x) ifelse(is.na(x), 0, x))
```

```{r clean-data}

episodes <- 
  all.df %>%
  mutate(
    age_group = case_when(
      age <= 18 ~ "0-18",
      age >= 19 & age <= 24 ~ "19-24",
      age >= 25 & age <= 34 ~ "25-34",
      age >= 35 & age <= 44 ~ "35-44",
      age >= 45 & age <= 55 ~ "45-55",
      TRUE ~ NA_character_
    ),
    state_tx = case_when(
      state == "TX" ~ "TX",
      state != "TX" ~ "Non-TX",
      TRUE ~ "Unknown"
    )
  ) %>%
  mutate(race_desc = recode(race_1,
    "R5" = "White",
    "R9" = "Other Race",
    "R1" = "American Indian/Alaska Native",
    "R2" = "Asian",
    "R3" = "Black/African American",
    "UN" = "Unknown/Not Specified",
    "R4" = "Native Hawaiian or Other Pacific Islander",
    .default = NA_character_
  )) %>%
  mutate(
    los_less_60 = case_when(los <= 60 ~ 1, TRUE ~ 0),
    monthly_anchor_date = as.Date(format(anchor_date, "%Y-%m-01"))
  ) %>%
  mutate(
    me_desc = case_when(
      me_code == "B" ~ "Pregnancy",
      me_code == "C" ~ "Emergency",
      me_code == "D" ~ "Other",
      me_code == "F" ~ "Other",
      me_code == "I" ~ "Institutional regular (CATS 1 3 or 4) (BP16 or 17)",
      me_code == "N" ~ "FFCHE (Former Foster Child in Higher Education)",
      me_code == "P" ~ "Three months prior",
      me_code == "Q" ~ "QMD coverage (Medicare only)",
      me_code == "R" ~ "Regular",
      me_code == "T" ~ "1929(b) Base plan 20 MAO client",
      me_code == "W" ~ "Healthy Texas Women",
      TRUE ~ "Unknown"
    )
  )
```

```{r filter-cohort}

cohort <- 
  episodes %>% 
  filter(age >= 19 & age <= 55) %>%
  filter(enrolled_birth == 1) %>%
  filter(state_tx == "TX") %>% 
  filter(los <= 60) %>%
  filter(prim_med_plan_mon == "Medicaid") %>%
  filter(prim_med_plan_design_mon != "HTW")

```

```{r add-time-vars}

cohort <- cohort %>%
  mutate(
    week_counter     = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "weeks")),
    biweekly_counter = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "days") / 14),
    monthly_counter  = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "days") / 30),
    anchor_date_week      = as.Date("2019-01-01") + week_counter * 7,
    anchor_date_twoweeks  = as.Date("2019-01-01") + biweekly_counter * 14,
    anchor_date_month     = floor_date(anchor_date, unit = "month")
  )

time_periods <- tibble::tibble(
  period = factor(
    c("Pre_period", "FFCRA", "Unwinding", "Exposure_Unwinding"),
    levels = c("Pre_period", "FFCRA", "Unwinding", "Exposure_Unwinding")
  ),
  start = as.Date(c("2019-01-01", "2020-01-01", "2023-04-01", "2022-04-01")),
  end   = as.Date(c("2019-12-31", "2022-03-31", "2023-08-31", "2023-08-31"))
)

covid_period <- tibble::tibble(
  period = "COVID",
  start  = as.Date("2020-03-01"),
  end    = as.Date("2020-12-31")
)

period_rects <- time_periods %>% select(start, end, period)

period_starts <- time_periods %>%
  select(date = start, period) %>%
  arrange(date) %>%
  mutate(period = factor(period, levels = period))

period_rects_non_overlap <- time_periods %>%
  mutate(
    end = case_when(
      period == "Exposure_Unwinding" ~ as.Date("2023-03-31"),
      TRUE ~ end
    )
  ) %>%
  select(start, end, period)

twelve_months_before <- as.Date("2025-08-31") %m-% months(12)

cohort <- cohort %>%
  mutate(
    period_Pre = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Pre_period") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Pre_period") %>% pull(end))
    ),
    period_FFCRA = as.integer(
      anchor_date >= (time_periods %>% filter(period == "FFCRA") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "FFCRA") %>% pull(end))
    ),
    period_Unwinding = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Unwinding") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Unwinding") %>% pull(end))
    ),
    period_Exposure_Unwinding = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Exposure_Unwinding") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Exposure_Unwinding") %>% pull(end))
    ),
    period_COVID = as.integer(
      anchor_date >= (covid_period %>% pull(start)) &
      anchor_date <= (covid_period %>% pull(end))
    )
  )

ffcra_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "FFCRA") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

exposure_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "Exposure_Unwinding") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

unwinding_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "Unwinding") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

cohort <- cohort %>%
  mutate(
    t = biweekly_counter,
    t_after_FFCRA     = pmax(0, t - ffcra_start_t),
    t_after_Exposure  = pmax(0, t - exposure_start_t),
    t_after_Unwinding = pmax(0, t - unwinding_start_t)
  )
```




# Cohort (Before Filtering to Mental Health)

Right now, APCD data goes until Aug 2025, so filtered anchor dates for 1 year before then. This will soon be updated to include more data, though. At this point, it is not filtered to "Regular" Medicaid. 

```{r}
cohort %>%
  filter(anchor_date <= twelve_months_before) %>%
  select(
    # Demographics
    mh_sample, outcome_type, anchor_year, age_group, me_desc,
    # Prior MH diagnosis categories (covariates, 280 days before anchor)
    mh_anxiety, mh_depression, mh_suicidal, mh_schizophrenia,
    mh_trauma, mh_bipolar, mh_neurodevelopmental, mh_other,
    # Postpartum MH diagnosis categories (outcomes, 0-12 months after anchor)
    out_mh_dx_12,
    out_mh_anxiety_12, out_mh_depression_12, out_mh_suicidal_12, out_mh_schizophrenia_12,
    out_mh_trauma_12, out_mh_bipolar_12, out_mh_neurodevelopmental_12, out_mh_other_12,
    # Enrollment
    ce_after_12, out_enroll_12,
    # MH treatment outcomes
    out_mh_drug_12, out_therapy_12
  ) %>%
  tbl_summary(
    label = list(
      mh_sample ~ "Mental Health Sample",
      outcome_type         ~ "Birth Outcome",
      anchor_year          ~ "Year",
      age_group            ~ "Age Group",
      me_desc              ~ "Enrollment Category",
      # race_desc            ~ "Race/Ethnicity",
      # Prior MH (covariates)
      mh_anxiety           ~ "Prior: Anxiety and fear-related disorders",
      mh_depression        ~ "Prior: Depressive disorders",
      mh_suicidal          ~ "Prior: Suicidal ideation/attempt/self-harm",
      mh_schizophrenia     ~ "Prior: Schizophrenia spectrum/psychotic disorders",
      mh_trauma            ~ "Prior: Trauma- and stressor-related disorders",
      mh_bipolar           ~ "Prior: Bipolar and related disorders",
      mh_neurodevelopmental ~ "Prior: Neurodevelopmental disorders",
      mh_other             ~ "Prior: Other disorders",
      # Postpartum MH diagnoses (outcomes)
      out_mh_dx_12              ~ "Postpartum: Any MH diagnosis (0-12 months)",
      out_mh_anxiety_12         ~ "Postpartum: Anxiety and fear-related disorders",
      out_mh_depression_12      ~ "Postpartum: Depressive disorders",
      out_mh_suicidal_12        ~ "Postpartum: Suicidal ideation/attempt/self-harm",
      out_mh_schizophrenia_12   ~ "Postpartum: Schizophrenia spectrum/psychotic disorders",
      out_mh_trauma_12          ~ "Postpartum: Trauma- and stressor-related disorders",
      out_mh_bipolar_12         ~ "Postpartum: Bipolar and related disorders",
      out_mh_neurodevelopmental_12 ~ "Postpartum: Neurodevelopmental disorders",
      out_mh_other_12           ~ "Postpartum: Other disorders",
      ce_after_12          ~ "Continuously enrolled 12 months post-delivery",
      out_enroll_12        ~ "Enrolled at 12 months post-delivery",
      out_mh_drug_12       ~ "MH prescription (0-12 months)",
      out_therapy_12       ~ "Therapy session (0-12 months)"
    )
  ) %>%
  as_flex_table() %>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  autofit() %>%
  FitFlextableToPage()
```


{{< pagebreak >}}


# MH Sub Cohort 

## Table 1

```{r make-mh-subgroup}

mh.subgroup <- 
  cohort %>% 
  filter(mh_sample == 1) %>%
  filter(anchor_date <= twelve_months_before)
```

```{r }

mh.subgroup %>%
  select(
    # Demographics
    outcome_type, anchor_year, age_group, me_desc,
    # Prior MH diagnosis categories (covariates, 280 days before anchor)
    mh_anxiety, mh_depression, mh_suicidal, mh_schizophrenia,
    mh_trauma, mh_bipolar, mh_neurodevelopmental, mh_other,
    # Postpartum MH diagnosis categories (outcomes, 0-12 months after anchor)
    out_mh_dx_12,
    out_mh_anxiety_12, out_mh_depression_12, out_mh_suicidal_12, out_mh_schizophrenia_12,
    out_mh_trauma_12, out_mh_bipolar_12, out_mh_neurodevelopmental_12, out_mh_other_12,
    # Enrollment
    ce_after_12, out_enroll_12,
    # MH treatment outcomes
    out_mh_drug_12, out_therapy_12
  ) %>%
  tbl_summary(
    label = list(
      outcome_type         ~ "Birth Outcome",
      anchor_year          ~ "Year",
      age_group            ~ "Age Group",
      me_desc              ~ "Enrollment Category",
      # race_desc            ~ "Race/Ethnicity",
      # Prior MH (covariates)
      mh_anxiety           ~ "Prior: Anxiety and fear-related disorders",
      mh_depression        ~ "Prior: Depressive disorders",
      mh_suicidal          ~ "Prior: Suicidal ideation/attempt/self-harm",
      mh_schizophrenia     ~ "Prior: Schizophrenia spectrum/psychotic disorders",
      mh_trauma            ~ "Prior: Trauma- and stressor-related disorders",
      mh_bipolar           ~ "Prior: Bipolar and related disorders",
      mh_neurodevelopmental ~ "Prior: Neurodevelopmental disorders",
      mh_other             ~ "Prior: Other disorders",
      # Postpartum MH diagnoses (outcomes)
      out_mh_dx_12              ~ "Postpartum: Any MH diagnosis (0-12 months)",
      out_mh_anxiety_12         ~ "Postpartum: Anxiety and fear-related disorders",
      out_mh_depression_12      ~ "Postpartum: Depressive disorders",
      out_mh_suicidal_12        ~ "Postpartum: Suicidal ideation/attempt/self-harm",
      out_mh_schizophrenia_12   ~ "Postpartum: Schizophrenia spectrum/psychotic disorders",
      out_mh_trauma_12          ~ "Postpartum: Trauma- and stressor-related disorders",
      out_mh_bipolar_12         ~ "Postpartum: Bipolar and related disorders",
      out_mh_neurodevelopmental_12 ~ "Postpartum: Neurodevelopmental disorders",
      out_mh_other_12           ~ "Postpartum: Other disorders",
      ce_after_12          ~ "Continuously enrolled 12 months post-delivery",
      out_enroll_12        ~ "Enrolled at 12 months post-delivery",
      out_mh_drug_12       ~ "MH prescription (0-12 months)",
      out_therapy_12       ~ "Therapy session (0-12 months)"
    )
  ) %>%
  as_flex_table() %>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  autofit() %>%
  FitFlextableToPage()
```



{{< pagebreak >}}

## Figure 1: MH Prescriptions 0-12 Months Postpartum

```{r fig-mh-drug}

mh.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_mh_drug_12 = mean(out_mh_drug_12, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_mh_drug_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth = 0.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "MH Prescription 0-12 Months Postpartum",
    x = "Date",
    y = "% Episodes with MH Prescription",
    color = "Period Start"
  )
```

{{< pagebreak >}}

## Figure 2: Therapy Sessions 0-12 Months Postpartum

```{r fig-therapy}

mh.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_therapy_12 = mean(out_therapy_12, na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_therapy_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth = 0.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Therapy 0-12 Months Postpartum",
    x = "Date",
    y = "% Episodes with Therapy Session",
    color = "Period Start"
  )
```

{{< pagebreak >}}

# Changelog: 

- 3/10/2026: Added postpartum MH DX outcomes and clarified language on prior labels. 
