---
title: "POEM TX Paper 2 (APCD Data) - MH Abstract ITS Results"
date: today
format: 
  docx:
    df-print: paged
    page-layout: full
    fig-width: 12
    fig-height: 8
    out-width: 100%
  html:
    fig-width: 12
    fig-height: 8
editor: source
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r setup}
#| echo: false
#| warning: false

# Load packages 
pacman::p_load(RPostgres, DBI, keyring, janitor, tidyverse, readxl,
               gtsummary, ggplot2, labelled, clipr, viridis, ggrepel, scales, ggthemes, flextable,
               odbc, openxlsx, beepr, tictoc, here, lubridate, patchwork, cowplot,
               sandwich, lmtest, broom)

#### Setup File Paths ####
current_dir <- here::here()

#### Database Connection 
greenplum_user = "jwozny"

apcd <- dbConnect(RPostgres::Postgres(),
                 dbname = "apcd_dev",
                 user = "jwozny",
                 password = key_get("apcd_dev", greenplum_user),
                 host = "spgpcdplv001",
                 bigint = "integer")

options(scipen = 999)

# Set Themes
my_theme <- function() {
  theme_minimal(base_size = 10) +
    theme(
      text = element_text(family = "sans", size=14),
      axis.text.y = element_text(size = 12, face="plain", margin = margin(r = 10, unit = "pt")),
      axis.title.y = element_text(size = 13, face = "bold", margin = margin(r = 20, unit = "pt")),
      axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 20, unit = "pt")),
      plot.caption = element_text(size = 12, face = "italic", margin = margin(t = 20, r=20, b = 5, l=20, unit = "pt"))
    )
}

set_flextable_defaults(padding=2.5)
theme_set(my_theme())

FitFlextableToPage <- function(ft, pgwidth = 6.5){
  ft_out <- ft %>% autofit()
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

# Table helpers (from paper 1)
mk_tbl <- function(fit) {
  tbl_regression(
    fit,
    intercept    = TRUE,
    pvalue_fun   = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 3),
    conf.int     = FALSE
  ) |>
    add_significance_stars(hide_p = TRUE, pattern = "{estimate}{stars}") |>
    modify_column_hide(columns = c(std.error))
}

compare_models <- function(model_names, spanners) {
  tbls <- lapply(model_names, function(nm) mk_tbl(models[[nm]]))
  tbl_merge(tbls = tbls, tab_spanner = spanners)
}

fmt_fun <- function(x) style_number(x, digits = 3)
```

```{r get-data}

all.df <- dbGetQuery(apcd, "
  select * from research_dev.poem_cohort_analysis2
;")

# Replace NAs
all.df[sapply(all.df, is.numeric)] <- 
  lapply(all.df[sapply(all.df, is.numeric)], function(x) ifelse(is.na(x), 0, x))
```

```{r clean-data}

episodes <- 
  all.df %>%
  mutate(
    age_group = case_when(
      age <= 18 ~ "0-18",
      age >= 19 & age <= 24 ~ "19-24",
      age >= 25 & age <= 34 ~ "25-34",
      age >= 35 & age <= 44 ~ "35-44",
      age >= 45 & age <= 55 ~ "45-55",
      TRUE ~ NA_character_
    ),
    state_tx = case_when(
      state == "TX" ~ "TX",
      state != "TX" ~ "Non-TX",
      TRUE ~ "Unknown"
    )
  ) %>%
  mutate(race_desc = recode(race_1,
    "R5" = "White",
    "R9" = "Other Race",
    "R1" = "American Indian/Alaska Native",
    "R2" = "Asian",
    "R3" = "Black/African American",
    "UN" = "Unknown/Not Specified",
    "R4" = "Native Hawaiian or Other Pacific Islander",
    .default = NA_character_
  )) %>%
  mutate(
    los_less_60 = case_when(los <= 60 ~ 1, TRUE ~ 0),
    monthly_anchor_date = as.Date(format(anchor_date, "%Y-%m-01"))
  ) %>%
  mutate(
    me_desc = case_when(
      me_code == "B" ~ "Pregnancy",
      me_code == "C" ~ "Emergency",
      me_code == "D" ~ "Other",
      me_code == "F" ~ "Other",
      me_code == "I" ~ "Institutional regular (CATS 1 3 or 4) (BP16 or 17)",
      me_code == "N" ~ "FFCHE (Former Foster Child in Higher Education)",
      me_code == "P" ~ "Three months prior",
      me_code == "Q" ~ "QMD coverage (Medicare only)",
      me_code == "R" ~ "Regular",
      me_code == "T" ~ "1929(b) Base plan 20 MAO client",
      me_code == "W" ~ "Healthy Texas Women",
      TRUE ~ "Unknown"
    )
  )
```

```{r filter-cohort}

cohort <- 
  episodes %>% 
  filter(age >= 19 & age <= 55) %>%
  filter(enrolled_birth == 1) %>%
  filter(state_tx == "TX") %>% 
  filter(los <= 60) %>%
  filter(prim_med_plan_mon == "Medicaid") %>%
  filter(prim_med_plan_design_mon != "HTW") %>%
  mutate(
    enroll_group = case_when(
      me_code == "R" ~ "Regular",
      me_code == "C" ~ "Emergency",
      TRUE ~ NA_character_
    ),
    treated = case_when(
      me_code == "R" ~ 1L,
      me_code == "C" ~ 0L,
      TRUE ~ NA_integer_
    )
  ) %>%
  filter(!is.na(enroll_group))
```

```{r add-time-vars}

cohort <- cohort %>%
  mutate(
    week_counter     = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "weeks")),
    biweekly_counter = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "days") / 14),
    monthly_counter  = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "days") / 30),
    anchor_date_week      = as.Date("2019-01-01") + week_counter * 7,
    anchor_date_twoweeks  = as.Date("2019-01-01") + biweekly_counter * 14,
    anchor_date_month     = floor_date(anchor_date, unit = "month")
  )

time_periods <- tibble::tibble(
  period = factor(
    c("Pre_period", "FFCRA", "Unwinding", "Exposure_Unwinding"),
    levels = c("Pre_period", "FFCRA", "Unwinding", "Exposure_Unwinding")
  ),
  start = as.Date(c("2019-01-01", "2020-01-01", "2023-04-01", "2022-04-01")),
  end   = as.Date(c("2019-12-31", "2022-03-31", "2023-08-31", "2023-08-31"))
)

covid_period <- tibble::tibble(
  period = "COVID",
  start  = as.Date("2020-03-01"),
  end    = as.Date("2020-12-31")
)

period_rects <- time_periods %>% select(start, end, period)

period_starts <- time_periods %>%
  select(date = start, period) %>%
  arrange(date) %>%
  mutate(period = factor(period, levels = period))

# Period start times (biweekly counter)
ffcra_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "FFCRA") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

twelve_months_before <- as.Date("2025-08-31") %m-% months(12)

cohort <- cohort %>%
  mutate(
    period_Pre = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Pre_period") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Pre_period") %>% pull(end))
    ),
    period_FFCRA = as.integer(
      anchor_date >= (time_periods %>% filter(period == "FFCRA") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "FFCRA") %>% pull(end))
    )
  ) %>%
  mutate(
    t = biweekly_counter,
    t_after_FFCRA = pmax(0, t - ffcra_start_t)
  )

# Filter to Pre + FFCRA periods only
cohort_its <- cohort %>%
  filter(period_Pre == 1 | period_FFCRA == 1) %>%
  filter(anchor_date <= twelve_months_before) %>%
  mutate(period_label = if_else(period_Pre == 1, "Pre (2019)", "FFCRA (2020-Mar 2022)"))

# Regular Medicaid only (treated) - main ITS
cohort_its_reg  <- cohort_its %>% filter(treated == 1)
mh.subgroup     <- cohort_its_reg %>% filter(mh_sample == 1)

# Emergency Medicaid only (control)
cohort_its_emg  <- cohort_its %>% filter(treated == 0)
mh.subgroup_emg <- cohort_its_emg %>% filter(mh_sample == 1)

# Both groups pooled - DiD ITS
cohort_its_did  <- cohort_its
mh.subgroup_did <- cohort_its_did %>% filter(mh_sample == 1)
```


# Descriptive Tables

## Table 1: Sample Characteristics

Age group, year of delivery, and Medicaid enrollment type for the analytic cohort (Pre + FFCRA periods).

```{r }

cohort_its <- cohort_its %>%
  mutate(
    delivery_year = factor(year(anchor_date)),
    age_group = factor(age_group, levels = c("19-24", "25-34", "35-44", "45-55"))
  )

cohort_its %>%
  mutate(
    delivery_year = factor(year(anchor_date)),
    age_group = factor(age_group, levels = c("19-24", "25-34", "35-44", "45-55"))
  ) %>%
  select(age_group, delivery_year, enroll_group, period_label) %>%
  tbl_summary(
    by = period_label,
    label = list(
      age_group     ~ "Age Group",
      delivery_year ~ "Year of Delivery",
      enroll_group  ~ "Medicaid Enrollment Type"
    )
  ) %>%
  add_overall() %>%
  as_flex_table() %>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  FitFlextableToPage()
```

{{< pagebreak >}}

## Table 2: Service Utilization by Period (Regular Medicaid only)

N (%) receiving each service in the Pre and FFCRA periods, for Regular Medicaid overall and the MH subgroup.

```{r }

desc_vars <- c("out_mh_drug_12", "out_therapy_12")
desc_labels <- list(
  out_mh_drug_12 ~ "MH Prescription (0-12 months)",
  out_therapy_12 ~ "Therapy Session (0-12 months)"
)

# Overall cohort by period
tbl_overall <- cohort_its_reg %>%
  select(period_label, all_of(desc_vars)) %>%
  tbl_summary(
    by = period_label,
    statistic = all_of(desc_vars) ~ "{n} ({p}%)",
    digits = all_of(desc_vars) ~ c(0, 1),
    label = desc_labels
  ) %>%
  add_overall() %>%
  modify_spanning_header(all_stat_cols() ~ "**Overall Cohort (Regular Medicaid)**")

# MH subgroup by period
tbl_mh <- mh.subgroup %>%
  select(period_label, all_of(desc_vars)) %>%
  tbl_summary(
    by = period_label,
    statistic = all_of(desc_vars) ~ "{n} ({p}%)",
    digits = all_of(desc_vars) ~ c(0, 1),
    label = desc_labels
  ) %>%
  add_overall() %>%
  modify_spanning_header(all_stat_cols() ~ "**MH Subgroup (Regular Medicaid)**")

tbl_merge(
  list(tbl_overall, tbl_mh),
  tab_spanner = c("**Overall Cohort**", "**MH Subgroup**")
) %>%
  as_flex_table() %>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  FitFlextableToPage()
```

{{< pagebreak >}}

# Descriptive Figures

## MH Prescriptions 0-12 Months Postpartum

```{r fig-drug}
#| fig-height: 6

bind_rows(
  cohort_its_reg %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(rate = mean(out_mh_drug_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(group = "Overall Cohort"),
  mh.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(rate = mean(out_mh_drug_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(group = "MH Subgroup")
) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = rate, color = group)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = as.Date("2020-01-01"),
             linetype = "dashed", color = "gray40", linewidth = 0.75) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_manual(values = c("Overall Cohort" = "#1f77b4", "MH Subgroup" = "#ff7f0e")) +
  annotate("text", x = as.Date("2020-02-01"), y = 0.95,
           label = "FFCRA Start", hjust = 0, size = 3.5, color = "gray40") +
  labs(
    title = "MH Prescription 0-12 Months Postpartum",
    subtitle = "Regular Medicaid, Pre and FFCRA periods",
    x = "Date", y = "% Episodes with MH Prescription", color = NULL
  )
```

{{< pagebreak >}}

## Therapy Sessions 0-12 Months Postpartum

```{r fig-therapy}
#| fig-height: 6

bind_rows(
  cohort_its_reg %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(rate = mean(out_therapy_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(group = "Overall Cohort"),
  mh.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(rate = mean(out_therapy_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(group = "MH Subgroup")
) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = rate, color = group)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = as.Date("2020-01-01"),
             linetype = "dashed", color = "gray40", linewidth = 0.75) +
  scale_y_continuous(labels = percent, limits = c(0, .5)) +
  scale_color_manual(values = c("Overall Cohort" = "#1f77b4", "MH Subgroup" = "#ff7f0e")) +
  annotate("text", x = as.Date("2020-02-01"), y = 0.48,
           label = "FFCRA Start", hjust = 0, size = 3.5, color = "gray40") +
  labs(
    title = "Therapy Sessions 0-12 Months Postpartum",
    subtitle = "Regular Medicaid, Pre and FFCRA periods",
    x = "Date", y = "% Episodes with Therapy Session", color = NULL
  )
```

{{< pagebreak >}}

# ITS Models 

```{r fit-models}

models <- list(

  # Regular Medicaid - overall cohort
  overall_drug_unadj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA,
    data = cohort_its_reg
  ),
  overall_drug_adj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA +
      age + no_transfusion_weight,
    data = cohort_its_reg
  ),
  overall_therapy_unadj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA,
    data = cohort_its_reg
  ),
  overall_therapy_adj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA +
      age + no_transfusion_weight,
    data = cohort_its_reg
  ),

  # Regular Medicaid - MH subgroup
  mh_drug_unadj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA,
    data = mh.subgroup
  ),
  mh_drug_adj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA +
      age + no_transfusion_weight,
    data = mh.subgroup
  ),
  mh_therapy_unadj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA,
    data = mh.subgroup
  ),
  mh_therapy_adj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA +
      age + no_transfusion_weight,
    data = mh.subgroup
  ),

  # DiD ITS - Regular vs Emergency pooled
  # R stores interactions as period_FFCRA:treated / t_after_FFCRA:treated
  did_drug_unadj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated,
    data = cohort_its_did
  ),
  did_drug_adj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated +
      age + no_transfusion_weight,
    data = cohort_its_did
  ),
  did_therapy_unadj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated,
    data = cohort_its_did
  ),
  did_therapy_adj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated +
      age + no_transfusion_weight,
    data = cohort_its_did
  ),
  did_mh_drug_unadj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated,
    data = mh.subgroup_did
  ),
  did_mh_drug_adj = lm(
    out_mh_drug_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated +
      age + no_transfusion_weight,
    data = mh.subgroup_did
  ),
  did_mh_therapy_unadj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated,
    data = mh.subgroup_did
  ),
  did_mh_therapy_adj = lm(
    out_therapy_12 ~ t + period_FFCRA + t_after_FFCRA +
      treated + period_FFCRA:treated + t_after_FFCRA:treated +
      age + no_transfusion_weight,
    data = mh.subgroup_did
  )
)
```

## Table 3: ITS Results - Regular Medicaid (Adjusted)

This is without Emergency control

Overall cohort and MH subgroup shown side by side for each outcome.

```{r }

its_labels <- list(
  t             ~ "Pre-trend",
  period_FFCRA  ~ "Level Change, FFCRA",
  t_after_FFCRA ~ "Trend Change, FFCRA"
)
its_include <- c("t", "period_FFCRA", "t_after_FFCRA")

mk_its_tbl <- function(model, header) {
  tbl_regression(model,
    include      = its_include,
    label        = its_labels,
    estimate_fun = fmt_fun
  ) %>%
    modify_column_hide(p.value) %>%
    modify_header(estimate ~ header)
}

tbl_merge(
  list(
    mk_its_tbl(models$overall_drug_adj,   "**Overall** Beta"),
    mk_its_tbl(models$mh_drug_adj,        "**MH Subgroup** Beta"),
    mk_its_tbl(models$overall_therapy_adj,"**Overall** Beta"),
    mk_its_tbl(models$mh_therapy_adj,     "**MH Subgroup** Beta")
  ),
  tab_spanner = c(
    "**MH Prescription**", "**MH Prescription**",
    "**Therapy Session**",  "**Therapy Session**"
  )
) %>%
  as_flex_table() %>%
  FitFlextableToPage()
```

{{< pagebreak >}}

# Difference-in-Differences 

## Figure: Regular vs Emergency Medicaid

```{r }
#| fig-height: 8

bind_rows(
  cohort_its_reg %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(drug = mean(out_mh_drug_12, na.rm = TRUE),
              therapy = mean(out_therapy_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(group = "Regular (Treated)"),
  cohort_its_emg %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(drug = mean(out_mh_drug_12, na.rm = TRUE),
              therapy = mean(out_therapy_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(group = "Emergency (Control)")
) %>%
  pivot_longer(cols = c(drug, therapy),
               names_to = "outcome",
               values_to = "rate") %>%
  mutate(outcome = recode(outcome,
    drug    = "MH Prescription",
    therapy = "Therapy Session"
  )) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = rate, color = group)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = as.Date("2020-01-01"),
             linetype = "dashed", color = "gray40", linewidth = 0.75) +
  scale_y_continuous(labels = percent) +
  scale_color_manual(values = c("Regular (Treated)" = "#1f77b4",
                                "Emergency (Control)" = "#d62728")) +
  facet_wrap(~ outcome, scales = "free_y", ncol = 1) +
  annotate("text", x = as.Date("2020-02-01"), y = Inf,
           label = "FFCRA Start", hjust = 0, vjust = 1.5, size = 3.5, color = "gray40") +
  labs(
    title = "MH Service Use: Regular vs Emergency Medicaid",
    subtitle = "Overall cohort, Pre and FFCRA periods",
    x = "Date", y = "% Episodes", color = NULL
  ) +
  theme(strip.text = element_text(size = 12, face = "bold"))
```

{{< pagebreak >}}

## Table 4: DiD ITS Results - Adjusted

These now include Emergency medicaid as control 

```{r }

did_labels <- list(
  t                       ~ "Pre-trend",
  period_FFCRA            ~ "Level Change, FFCRA (Control)",
  t_after_FFCRA           ~ "Trend Change, FFCRA (Control)",
  treated                 ~ "Regular vs Emergency (baseline)",
  `period_FFCRA:treated`  ~ "DiD Level Change, FFCRA",
  `t_after_FFCRA:treated` ~ "DiD Trend Change, FFCRA"
)
did_include <- c("t", "period_FFCRA", "t_after_FFCRA",
                 "treated", "period_FFCRA:treated", "t_after_FFCRA:treated")

mk_did_tbl <- function(model, header) {
  tbl_regression(model,
    include      = did_include,
    label        = did_labels,
    estimate_fun = fmt_fun
  ) %>%
    modify_column_hide(p.value) %>%
    modify_header(estimate ~ header)
}

tbl_merge(
  list(
    mk_did_tbl(models$did_drug_adj,       "**Overall** Beta"),
    mk_did_tbl(models$did_mh_drug_adj,    "**MH Subgroup** Beta"),
    mk_did_tbl(models$did_therapy_adj,    "**Overall** Beta"),
    mk_did_tbl(models$did_mh_therapy_adj, "**MH Subgroup** Beta")
  ),
  tab_spanner = c(
    "**MH Prescription**", "**MH Prescription**",
    "**Therapy Session**",  "**Therapy Session**"
  )
) %>%
  as_flex_table() %>%
  FitFlextableToPage()
```
