---
title: "POEM TX Paper 1 (APCD Data)"
date: today
format: 
  docx:
    df-print: paged
    page-layout: full
    fig-width: 12
    fig-height: 8
    out-width: 100%
  html:
    fig-width: 12
    fig-height: 8
editor: source
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r setup}
#| echo: false
#| warning: false
#| 

# Load packages 
pacman::p_load(RPostgres, DBI, keyring, janitor, tidyverse, readxl,
               gtsummary, ggplot2, labelled, clipr, viridis, ggrepel, scales, ggthemes, flextable, DiagrammeR,
               odbc, openxlsx, beepr, tictoc, here, sandwich, lmtest, lubridate, patchwork, ggnewscale, cowplot)

#### Setup File Paths ####
# Get the location of this current .R file 
current_dir <- here::here()

#### Database Connection 
greenplum_user = "jwozny" #this is for keyring to go get your password info so you don't have to write it in the file

#Connect to Greenplum
apcd <- dbConnect(RPostgres::Postgres(),
                 dbname = "apcd_dev",
                 user = "jwozny",
                 password = key_get("apcd_dev", greenplum_user),
                 host = "spgpcdplv001",
                 bigint = "integer")

options(scipen = 999)


# Set Themes
my_theme <- function() {
  theme_minimal(base_size = 10) +
    theme(
      text = element_text(family = "sans", size=14),
      axis.text.y = element_text(size = 12, face="plain", margin = margin(r = 10, unit = "pt")),
      axis.title.y = element_text(size = 13, face = "bold", margin = margin(r = 20, unit = "pt")) ,
      axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 20, unit = "pt")) , 
      plot.caption = element_text(size = 12, face = "italic", margin = margin(t = 20, r=20, b = 5, l=20, unit = "pt"))
    )
}

set_flextable_defaults(padding=2.5)

theme_set(my_theme())

# Flextable fix
FitFlextableToPage <- function(ft, pgwidth = 6.5){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}


```

```{r get-outcomes}

# Get from DB
all.df <- dbGetQuery(apcd, " 
  select * from research_dev.poem_cohort_analysis1 
 ;")

# Replace NAs
all.df[sapply(all.df, is.numeric)] <- 
  lapply(all.df[sapply(all.df, is.numeric)], function(x) ifelse(is.na(x), 0, x))

```

```{r clean-data}

# Grab Data 
episodes <- 
  all.df %>%
  mutate(
    age_group = case_when(
    age <= 18 ~ "0-18",
    age >= 19 & age <= 24 ~ "19-24",
    age >= 25 & age <= 34 ~ "25-34",
    age >= 35 & age <= 44 ~ "35-44",
    age >= 45 & age <= 55 ~ "45-55",
    TRUE ~ NA_character_
  ),
     state_tx = case_when(
      state == "TX" ~ "TX",
      state != "TX" ~ "Non-TX",
      TRUE ~ "Unknown"
    )
  ) %>%
  mutate(race_desc = recode(race_1,
    "R5" = "White",
    "R9" = "Other Race",
    "R1" = "American Indian/Alaska Native",
    "R2" = "Asian",
    "R3" = "Black/African American",
    "UN" = "Unknown/Not Specified",
    "R4" = "Native Hawaiian or Other Pacific Islander",
    .default = NA_character_
  )) %>%
  mutate(los_less_60 = case_when(
    los <= 60 ~ 1,
    TRUE ~ 0
  )) %>%
  mutate(monthly_anchor_date = as.Date(format(anchor_date, "%Y-%m-01")))

# #Label
# var_label(episodes) <- list(
#     anchor_year = "Year",
#     age = "Age",
#     race_desc = "Race/Ethnicity",
#     age_group = "Age Group",
#     me_desc = "Enrollment Category (Month of birth episode)",
#     state_tx = "State (Month of birth episode)",
#     outcome_type = "Birth Outcome",
#     los = "Length of Stay",
#     hispanic = "Hispanic",
#     los_less_60 = "LOS <= 60 days",
#     diab_sample = "Diabetes Sample",
#     htn_sample = "HTN Sample",
#     monthly_anchor_date = "Anchor Month",
#     no_transfusion_weight = "Index No Transfusion Weight",
#     plan_ = "Plan",
#     dual = "Dual"
#   )


```

```{r filter-cohort-overall}

cohort <- 
episodes %>% 
  filter(age >= 19 & age <= 55) %>%
  filter(enrolled_birth == 1) %>%
  filter(state_tx == 'TX') %>% 
  filter(los <= 60) %>%
  filter( prim_med_plan_mon == "Medicaid") %>%
  filter(prim_med_plan_design_mon != "HTW")

cohort %>% nrow()
  
```



```{r add-time-vars}

# Counters and anchor dates (START AT 0)
cohort <- cohort %>%
  mutate(
    week_counter = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "weeks")),
    biweekly_counter = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "days") / 14),
    monthly_counter = as.integer(difftime(anchor_date, as.Date("2019-01-01"), units = "days") / 30),

    anchor_date_week     = as.Date("2019-01-01") + week_counter * 7,
    anchor_date_twoweeks = as.Date("2019-01-01") + biweekly_counter * 14,
    anchor_date_month    = floor_date(anchor_date, unit = "month")
  )

# Create time periods
time_periods <- tibble::tibble(
  period = factor(
    c("Pre_period", "FFCRA", "Unwinding", "Exposure_Unwinding"),
    levels = c("Pre_period", "FFCRA", "Unwinding", "Exposure_Unwinding")
  ),
  start = as.Date(c("2019-01-01", "2020-01-01", "2023-04-01", "2022-04-01")),
  end   = as.Date(c("2019-12-31", "2022-03-31", "2023-08-31", "2023-08-31"))
)

# COVID period for sensitivity analysis (kept separate)
covid_period <- tibble::tibble(
  period = "COVID",
  start  = as.Date("2020-03-01"),
  end    = as.Date("2020-12-31")
)

# Create separate df for graphs later on
period_rects <- time_periods %>%
  select(start, end, period)

# Get a date twelve months before end of FY24
twelve_months_before <- as.Date("2024-08-31") %m-% months(12)

# Create indicators
# note we don't actually use the pre_period one...
cohort <- cohort %>%
  mutate(
    period_Pre = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Pre_period") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Pre_period") %>% pull(end))
    ),
    period_FFCRA = as.integer(
      anchor_date >= (time_periods %>% filter(period == "FFCRA") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "FFCRA") %>% pull(end))
    ),
    period_Unwinding = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Unwinding") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Unwinding") %>% pull(end))
    ),
    period_Exposure_Unwinding = as.integer(
      anchor_date >= (time_periods %>% filter(period == "Exposure_Unwinding") %>% pull(start)) &
      anchor_date <= (time_periods %>% filter(period == "Exposure_Unwinding") %>% pull(end))
    ),
    period_COVID = as.integer(
      anchor_date >= (covid_period %>% pull(start)) &
      anchor_date <= (covid_period %>% pull(end))
    )
  )

# Starts

ffcra_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "FFCRA") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

exposure_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "Exposure_Unwinding") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

unwinding_start_t <- as.integer(
  difftime(time_periods %>% filter(period == "Unwinding") %>% pull(start),
           as.Date("2019-01-01"), units = "days") / 14
)

cohort <- cohort %>%
  mutate(
    t = biweekly_counter,

    t_after_FFCRA     = pmax(0, t - ffcra_start_t),
    t_after_Exposure  = pmax(0, t - exposure_start_t),
    t_after_Unwinding = pmax(0, t - unwinding_start_t)
  )

# Check overlap
cohort_check <- cohort %>%
  mutate(
    period_sum = period_Pre + period_FFCRA + period_Unwinding 
  )

stopifnot(max(cohort_check$period_sum, na.rm = TRUE) <= 1)


```

# Main Analysis Tables and Figures

## Table 1

```{r filter-cohort}

sub.cohort <- 
cohort %>% filter(htn_sample==1 | diab_sample==1)  %>%
  filter(anchor_date <= twelve_months_before)

```

```{r}
# Make long version
long_subcohort <- sub.cohort %>%
  mutate(id = row_number()) %>%
  pivot_longer(cols = c(htn_sample, diab_sample), 
               names_to = "group", 
               values_to = "in_group") %>%
  filter(in_group == 1)

# Table by group 
table_by_group <- long_subcohort %>%
  mutate(group = recode(group,
                        htn_sample = "Hypertension",
                        diab_sample = "Diabetes")) %>%
  select(group, outcome_type, anchor_year, age_group, no_transfusion_weight) %>%
  tbl_summary(by = group)

# Overall
table_overall <- sub.cohort %>%
  select(outcome_type, anchor_year, age_group, no_transfusion_weight) %>%
  tbl_summary()

# Merge 
merged_table <- tbl_merge(
  tbls = list(table_overall, table_by_group),
  tab_spanner = c("**Overall**", "**By Condition**")
)


merged_table %>%
  as_flex_table() %>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  autofit() %>%
  FitFlextableToPage()

```

```{r make-htn}
htn.subgroup <- 
  cohort %>% filter(htn_sample==1) %>%
  filter(anchor_date <= twelve_months_before)
```

```{r make-diab}
diab.subgroup <- 
  cohort %>% 
  filter(diab_sample==1) %>%
  filter(anchor_date <= twelve_months_before)
```

{{< pagebreak >}}

## Figure 1: Biweekly graphs based on anchor date: outpatient utilization

```{r}
# Get summary 
visit.plots.subgroups_any <- bind_rows(
  htn.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(Any_Outpatient = mean(out_any_outpatient_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(subgroup = "Hypertension"),
  diab.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(Any_Outpatient = mean(out_any_outpatient_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(subgroup = "Diabetes")
) %>%
  mutate(subgroup = factor(subgroup, levels = c("Hypertension", "Diabetes")))

```

```{r}

# Create non-overlapping period rectangles
period_rects_non_overlap <- time_periods %>%
  mutate(
    end = case_when(
      period == "Exposure_Unwinding" ~ as.Date("2023-03-31"),  # End before Unwinding starts
      TRUE ~ end
    )
  ) %>%
  select(start, end, period)


ggplot() +
  geom_rect(
    data = period_rects_non_overlap,
    aes(xmin = start, xmax = end, ymin = 0, ymax = 1, fill = period),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  geom_line(
    data = visit.plots.subgroups_any,
    aes(x = anchor_date_twoweeks, y = Any_Outpatient, group = 1),
    linewidth = 1,
    color = "black",
    show.legend = FALSE
  ) +
  scale_fill_manual(
    name = "Time Period",
    values = c(
      "Pre_period" = "lightpink",
      "FFCRA" = "steelblue",
      "Unwinding" = "tan3",
      "Exposure_Unwinding" = "lightgreen"
    )
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  facet_wrap(~ subgroup, ncol = 2) +
  labs(
    title = "Any Outpatient Visit - 12 Months Post-Delivery",
    x = "Date",
    y = "% Episodes with Any Outpatient Visit"
  ) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 12, face = "bold")
  )

```

{{< pagebreak >}}

## Figure 2: Biweekly graphs based on anchor date: diabetes screening

```{r}

# Get period starts
period_starts <- time_periods %>%
  select(date = start, period) %>%
  arrange(date) %>%
  mutate(period = factor(period, levels = period))

diab.screening <- 
diab.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_diab_screen_12 = mean(out_diab_screen_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_diab_screen_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Diabetes Screening Rates 12 Months",
    x = "Date",
    y = "% Episode with Screening",
    color = "Period Start"
  ) +
  theme_minimal()

# Diabetes Visit graph
diab.visit <- 
diab.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_postpartum_12 = mean(out_postpartum_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_postpartum_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Diabetes Subgroup Postpartum Visit 12 Months",
    x = "Date",
    y = "% Episodes with visit",
    color = "Period Start"
  ) +
  theme_minimal()

# HTN Visit graph
htn.visit <- 
htn.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_postpartum_12 = mean(out_postpartum_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_postpartum_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Hypertension Subgroup Postpartum Visit 12 Months",
    x = "Date",
    y = "% Episodes with visit",
    color = "Period Start"
  ) +
  theme_minimal()


htn.med <- 
htn.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_htn_med_12 = mean(out_htn_med_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_htn_med_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Hypertension Subgroup Medication 12 Months",
    x = "Date",
    y = "% Episodes with medication",
    color = "Period Start"
  ) +
  theme_minimal()

```

```{r}
diab.screening
```

{{< pagebreak >}}

## Figure 3: Biweekly graphs based on anchor date: hypertensive medication

```{r}
htn.med
```

```{r fit-regressions}
models <- list(
  # Diabetes Screening
  diab_screen_unadj = lm(
    out_diab_screen_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure,
    data = diab.subgroup
  ),
  diab_screen_adj = lm(
    out_diab_screen_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure +
      age + no_transfusion_weight,
    data = diab.subgroup
  ),

  # Diabetes Postpartum Visits
  diab_postpartum_unadj = lm(
    out_postpartum_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure,
    data = diab.subgroup
  ),
  diab_postpartum_adj = lm(
    out_postpartum_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure +
      age + no_transfusion_weight,
    data = diab.subgroup
  ),

  # Diabetes Any Outpatient Visits
  diab_any_outpatient_unadj = lm(
    out_any_outpatient_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure,
    data = diab.subgroup
  ),
  diab_any_outpatient_adj = lm(
    out_any_outpatient_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure +
      age + no_transfusion_weight,
    data = diab.subgroup
  ),

  # HTN Medication
  htn_med_unadj = lm(
    out_htn_med_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure,
    data = htn.subgroup
  ),
  htn_med_adj = lm(
    out_htn_med_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure +
      age + no_transfusion_weight,
    data = htn.subgroup
  ),

  # HTN Postpartum Visits
  htn_postpartum_unadj = lm(
    out_postpartum_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure,
    data = htn.subgroup
  ),
  htn_postpartum_adj = lm(
    out_postpartum_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure +
      age + no_transfusion_weight,
    data = htn.subgroup
  ),

  # HTN Any Outpatient Visits
  htn_any_outpatient_unadj = lm(
    out_any_outpatient_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure,
    data = htn.subgroup
  ),
  htn_any_outpatient_adj = lm(
    out_any_outpatient_12 ~ t + period_FFCRA + period_Exposure_Unwinding +
      t_after_FFCRA + t_after_Exposure +
      age + no_transfusion_weight,
    data = htn.subgroup
  )
)


```

{{< pagebreak >}}

## Table 2: ITS results of all utilization outcomes, adjusted, main coefficients only

```{r}
# helper to rename slope-change rows (now using centered clocks, not interactions)
fix_trend_labels <- function(tbl) {
  tbl %>%
    modify_table_body(~ .x %>%
      dplyr::mutate(
        label = dplyr::case_when(
          variable == "t_after_FFCRA"    ~ "Trend Change, FFCRA",
          variable == "t_after_Exposure" ~ "Trend Change, Exposure to Unwinding",
          TRUE ~ label
        )
      )
    )
}

# settings for formatting
fmt_fun <- function(x) style_number(x, digits = 3)

# Diabetes: Screening
diab_screen_tbl <- tbl_regression(
  models$diab_screen_adj,
  include = c("t", "period_FFCRA", "period_Exposure_Unwinding", "t_after_FFCRA", "t_after_Exposure"),
  label = list(
    t ~ "Pre-trend",
    period_FFCRA ~ "Level Change, FFCRA",
    t_after_FFCRA ~ "Trend Change, FFCRA",
    period_Exposure_Unwinding ~ "Level Change, Exposure to Unwinding",
    t_after_Exposure ~ "Trend Change, Exposure to Unwinding"
  ),
  estimate_fun = fmt_fun
) %>%
  modify_column_hide(p.value) %>%
  modify_header(estimate ~ "**Diabetes Screening** Beta") %>%
  fix_trend_labels()

# Diabetes: Any outpatient utilization
diab_outpatient_tbl <- tbl_regression(
  models$diab_any_outpatient_adj,
  include = c("t", "period_FFCRA", "period_Exposure_Unwinding", "t_after_FFCRA", "t_after_Exposure"),
  label = list(
    t ~ "Pre-trend",
    period_FFCRA ~ "Level Change, FFCRA",
    t_after_FFCRA ~ "Trend Change, FFCRA",
    period_Exposure_Unwinding ~ "Level Change, Exposure to Unwinding",
    t_after_Exposure ~ "Trend Change, Exposure to Unwinding"
  ),
  estimate_fun = fmt_fun
) %>%
  modify_column_hide(p.value) %>%
  modify_header(estimate ~ "**Any outpatient utilization** Beta") %>%
  fix_trend_labels()

# Hypertension: Medication
htn_med_tbl <- tbl_regression(
  models$htn_med_adj,
  include = c("t", "period_FFCRA", "period_Exposure_Unwinding", "t_after_FFCRA", "t_after_Exposure"),
  label = list(
    t ~ "Pre-trend",
    period_FFCRA ~ "Level Change, FFCRA",
    t_after_FFCRA ~ "Trend Change, FFCRA",
    period_Exposure_Unwinding ~ "Level Change, Exposure to Unwinding",
    t_after_Exposure ~ "Trend Change, Exposure to Unwinding"
  ),
  estimate_fun = fmt_fun
) %>%
  modify_column_hide(p.value) %>%
  modify_header(estimate ~ "**Antihypertensive medication** Beta") %>%
  fix_trend_labels()

# Hypertension: Any outpatient utilization
htn_outpatient_tbl <- tbl_regression(
  models$htn_any_outpatient_adj,
  include = c("t", "period_FFCRA", "period_Exposure_Unwinding", "t_after_FFCRA", "t_after_Exposure"),
  label = list(
    t ~ "Pre-trend",
    period_FFCRA ~ "Level Change, FFCRA",
    t_after_FFCRA ~ "Trend Change, FFCRA",
    period_Exposure_Unwinding ~ "Level Change, Exposure to Unwinding",
    t_after_Exposure ~ "Trend Change, Exposure to Unwinding"
  ),
  estimate_fun = fmt_fun
) %>%
  modify_column_hide(p.value) %>%
  modify_header(estimate ~ "**Any outpatient utilization** Beta") %>%
  fix_trend_labels()

# Merge within cohort (unchanged)
diabetes_merged <- tbl_merge(
  list(diab_screen_tbl, diab_outpatient_tbl),
  tab_spanner = c("**Diabetes cohort**", "**Diabetes cohort**")
) %>%
  modify_spanning_header(everything() ~ "**Diabetes cohort**")

htn_merged <- tbl_merge(
  list(htn_med_tbl, htn_outpatient_tbl),
  tab_spanner = c("**Hypertension cohort**", "**Hypertension cohort**")
) %>%
  modify_spanning_header(everything() ~ "**Hypertension cohort**")

```

```{r}
diabetes_merged %>% as_flex_table()%>% FitFlextableToPage()
```

```{r}
htn_merged %>% as_flex_table() %>% FitFlextableToPage()
```

{{< pagebreak >}}

# Supplemental Figures

## Flowchart

<!-- ```{r} -->
<!-- library(DiagrammeR) -->
<!-- library(DiagrammeRsvg) -->
<!-- library(webshot) -->

<!-- # cohort copy -->
<!-- final_cohort <- cohort -->

<!-- # Count cohort steps -->
<!-- n0 <- nrow(episodes) -->
<!-- n1 <- episodes %>% filter(age >= 19 & age <= 55) %>% nrow() -->
<!-- n2 <- episodes %>% filter(age >= 19 & age <= 55, enrolled_birth == 1) %>% nrow() -->
<!-- n3 <- episodes %>% filter(age >= 19 & age <= 55, enrolled_birth == 1, state_tx == "TX") %>% nrow() -->
<!-- n4 <- episodes %>% filter(age >= 19 & age <= 55, enrolled_birth == 1, state_tx == "TX", los <= 60) %>% nrow() -->
<!-- n5 <- nrow(final_cohort) -->
<!-- n5_diab <- final_cohort %>% filter(diab_sample == 1) %>% nrow() -->
<!-- n5_htn  <- final_cohort %>% filter(htn_sample == 1) %>% nrow() -->

<!-- # Create and export the updated diagram -->
<!-- svg_code <- export_svg( -->
<!--   grViz(sprintf(" -->
<!--     digraph cohort_flow { -->
<!--       graph [layout = dot, rankdir = TB] -->
<!--       node [shape = box, style = filled, fillcolor = LightGray, fontname = Helvetica, width = 3] -->

<!--       A [label = 'Initial episodes\\n(n = %d)'] -->
<!--       B [label = 'Aged 19-55\\n(n = %d)'] -->
<!--       C [label = 'Enrolled at birth\\n(n = %d)'] -->
<!--       D [label = 'Texas residents\\n(n = %d)'] -->
<!--       E [label = 'LOS <= 60 days\\n(n = %d)'] -->
<!--       F [label = 'Enrollment filters\\n(n = %d)'] -->
<!--       G [label = 'Diabetes sample\\n(n = %d)'] -->
<!--       H [label = 'Hypertension sample\\n(n = %d)'] -->

<!--       A -> B -> C -> D -> E -> F -->
<!--       F -> G -->
<!--       F -> H -->
<!--     } -->
<!--   ", n0, n1, n2, n3, n4, n5, n5_diab, n5_htn)) -->
<!-- ) -->

<!-- #  SVG to file -->
<!-- writeLines(svg_code, "flowchart.svg") -->

<!-- # SVG to PNG -->
<!-- webshot::webshot("flowchart.svg", file = "flowchart.png", vwidth = 1000, vheight = 900) -->
<!-- ``` -->

{{< pagebreak >}}

## Enrollment

```{r}
# Summary
enrollment.subgroups <- bind_rows(
  htn.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(
      enrollment = mean(out_enroll_12, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(subgroup = "Hypertension"),
  
  diab.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(
      enrollment = mean(out_enroll_12, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(subgroup = "Diabetes")
)

# Graph
enrollment.subgroups %>%
  ggplot(aes(x = anchor_date_twoweeks, y = enrollment)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  facet_wrap(~ subgroup, ncol = 2) +
  labs(
    title = "Enrollment Rates 12 Months Later",
    x = "Date",
    y = "% Episodes enrolled 12 months after delivery",
    color = "Period Start"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 12, face = "bold")
  )
```

{{< pagebreak >}}

```{r}
# Summary
enrollment.subgroups.ce <- bind_rows(
  htn.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(
      enrollment = mean(ce_after_12, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(subgroup = "Hypertension"),
  
  diab.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(
      enrollment = mean(ce_after_12, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(subgroup = "Diabetes")
)

#Graph
enrollment.subgroups.ce %>%
  ggplot(aes(x = anchor_date_twoweeks, y = enrollment)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  facet_wrap(~ subgroup, ncol = 2) +
  labs(
    title = "Continuous Enrollment for 12 Months",
    x = "Date",
    y = "% Episode with CE for 12 months after delivery",
    color = "Period Start"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 12, face = "bold")
  )
```

{{< pagebreak >}}

## OGT vs A1C

```{r diab-test-types}

# Summary
diab.both.tests <- 
bind_rows(
 diab.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(screening_rate = mean(out_diab_screen_hba1c_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(test_type = "A1c")
,
 diab.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(screening_rate = mean(out_diab_screen_gtt_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(test_type = "OGTT")
)

# graph
diab.both.tests %>%
  ggplot(aes(x = anchor_date_twoweeks, y = screening_rate, color = test_type)) +
  geom_line(linewidth = 1) +
  geom_rect(
    data = period_rects_non_overlap,
    aes(xmin = start, xmax = end, ymin = 0, ymax = Inf, fill = period),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set1") +
  labs(
    title = "Diabetes Screening Rates 12 Months (OGTT vs A1c)",
    x = "Date",
    y = "% Episode with Screening",
  ) +
  theme_minimal()

```

{{< pagebreak >}}

## Average Visits per Person

```{r}

# Summary
visit.counts.subgroups_any <- bind_rows(
  htn.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(Any_Outpatient = mean(total_visit_days_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(subgroup = "Hypertension"),
  diab.subgroup %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(Any_Outpatient = mean(total_visit_days_12, na.rm = TRUE), .groups = "drop") %>%
    mutate(subgroup = "Diabetes")
) %>%
  mutate(subgroup = factor(subgroup, levels = c("Hypertension", "Diabetes")))

# Graph
ggplot() +
  geom_rect(
    data = period_rects_non_overlap,
    aes(xmin = start, xmax = end, ymin = 0, ymax = Inf, fill = period),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  geom_line(
    data = visit.counts.subgroups_any,
    aes(x = anchor_date_twoweeks, y = Any_Outpatient, group = 1),
    linewidth = 1,
    color = "black",
    show.legend = FALSE
  ) +
  scale_fill_manual(
    name = "Time Period",
    values = c(
      "Pre_period" = "lightpink",
      "FFCRA" = "steelblue",
      "Unwinding" = "tan3",
      "Exposure_Unwinding" = "lightgreen"
    )
  ) +
  scale_y_continuous(limits = c(0, NA)) +
  facet_wrap(~ subgroup, ncol = 2) +
  labs(
    title = "Any Outpatient - Average Number of Visits (12 Months Post-Delivery)",
    x = "Date",
    y = "Average Number of Visits"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 12, face = "bold")
  )

```

{{< pagebreak >}}

# Supplemental Tables

## Full ITS Results

### Diabetes Screening

Unadjusted

```{r}
tbl_regression(models$diab_screen_unadj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 
```

Adjusted

```{r}

tbl_regression(models$diab_screen_adj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

### Diabetes Outpatient

Unadjusted

```{r}
tbl_regression(models$diab_any_outpatient_unadj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 
```

Adjusted

```{r}

tbl_regression(models$diab_any_outpatient_adj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

{{< pagebreak >}}

### HTN Medication

Unadjusted

```{r}
tbl_regression(models$htn_med_unadj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
)

```

Adjusted

```{r}
tbl_regression(models$htn_med_adj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
)
```

{{< pagebreak >}}

### HTN Outpatient

Unadjusted

```{r}
tbl_regression(models$htn_any_outpatient_unadj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 
```

Adjusted

```{r}

tbl_regression(models$htn_any_outpatient_adj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

{{< pagebreak >}}

## HEDIS Postpartum Visits

### Diabetes Postpartum Visits

Unadjusted

```{r}
tbl_regression(models$diab_postpartum_unadj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

Adjusted

```{r}

tbl_regression(models$diab_postpartum_adj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
)

```

### HTN Postpartum Visits

Unadjusted

```{r}
tbl_regression(models$htn_postpartum_unadj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
)

```

Adjusted

```{r}

tbl_regression(models$htn_postpartum_adj,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
)

```

{{< pagebreak >}}

## Event Study

```{r graph-ce-2}
# Filter
cohort_filtered <- cohort %>% 
  filter(anchor_date >= as.Date("2020-01-01") & anchor_date < as.Date("2023-08-31"))


outcome_ce <- cohort_filtered %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(
    mean_ce_after_12 = mean(ce_after_12, na.rm = TRUE),
    .groups = "drop"
  )

# Plot outcome over time
ggplot(outcome_ce, aes(x = anchor_date_twoweeks, y = mean_ce_after_12)) +
  geom_line(linewidth = 1, color = "darkblue") +
  geom_point(color = "darkblue", alpha = 0.6) +
  labs(
    title = "Continuous Enrollment (Filtered for 2020)",
    x = "Biweek Period",
    y = "% CE After 12",
    size = "N"
  ) +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 10, color = "gray40"),
    axis.title = element_text(size = 11, face = "bold")
  )

```

```{r graph-ce}
test_unwinding_dates_simple <- function(data,
                                        outcome_var = "ce_after_12",
                                        baseline_start = as.Date("2020-01-01"),
                                        unwinding_test_start = as.Date("2021-01-01"),
                                        unwinding_test_end = as.Date("2023-04-14"),
                                        data_end_date = as.Date("2023-08-31"),
                                        interval_days = 14) {

  # sequence of potential unwinding start dates
  test_dates <- seq(from = unwinding_test_start,
                    to   = unwinding_test_end,
                    by   = interval_days)

  # Function to fit models for a given unwinding start date
  fit_model_for_date <- function(unwind_start, data) {

    # Baseline ends the day BEFORE unwinding starts
    baseline_end <- unwind_start - 1

    # mutually exclusive period indicators + 0-based global time (t)
    data_temp <- data %>%
      mutate(
        period_Baseline = as.integer(anchor_date >= baseline_start & anchor_date <= baseline_end),
        period_PostUnwinding = as.integer(anchor_date >= unwind_start & anchor_date <= data_end_date)
      ) %>%
      filter(period_Baseline == 1 | period_PostUnwinding == 1) %>%
      mutate(
        # 0-based time since baseline_start (your baseline clock)
        t = as.integer(difftime(anchor_date, baseline_start, units = "days") / 14),

        # 0-based "time since unwinding start" clock (proper ITS parameterization)
        unwind_start_t = as.integer(difftime(unwind_start, baseline_start, units = "days") / 14),
        t_after_unwinding = pmax(0, t - unwind_start_t)
      )

    # check mutually exclusive
    check_sum <- data_temp %>%
      mutate(period_sum = period_Baseline + period_PostUnwinding) %>%
      pull(period_sum)

    if (any(check_sum != 1)) {
      warning(paste("Periods not mutually exclusive for date:", unwind_start))
    }

    # Model 1: ITS model with correct centered slope term
    # Y = B0 + B1*t + B2*Post + B3*(t - Ti)*Post
    model_its <- lm(
      as.formula(paste0(outcome_var, " ~ t + period_PostUnwinding + t_after_unwinding")),
      data = data_temp
    )

    # Model 2: Simple pre/post model (no time trends)
    model_prepost <- lm(
      as.formula(paste0(outcome_var, " ~ period_PostUnwinding")),
      data = data_temp
    )

    # Extract coefficients for ITS model
    coef_its <- broom::tidy(model_its)
    b0_its <- coef_its %>% filter(term == "(Intercept)")
    b1_its <- coef_its %>% filter(term == "t")
    b2_its <- coef_its %>% filter(term == "period_PostUnwinding")
    b3_its <- coef_its %>% filter(term == "t_after_unwinding")

    # Extract coefficients for pre/post model
    coef_prepost <- broom::tidy(model_prepost)
    intercept_prepost <- coef_prepost %>% filter(term == "(Intercept)")
    effect_prepost <- coef_prepost %>% filter(term == "period_PostUnwinding")

    # Return results
    tibble(
      unwinding_start_date = unwind_start,
      baseline_end_date = baseline_end,
      n_baseline = sum(data_temp$period_Baseline == 1),
      n_postunwinding = sum(data_temp$period_PostUnwinding == 1),

      # ITS model results
      its_intercept = b0_its$estimate,
      its_time_trend = b1_its$estimate,
      its_level_change = b2_its$estimate,
      its_level_se = b2_its$std.error,
      its_level_pval = b2_its$p.value,
      its_level_ci_lower = its_level_change - 1.96 * its_level_se,
      its_level_ci_upper = its_level_change + 1.96 * its_level_se,
      its_slope_change = b3_its$estimate,
      its_slope_se = b3_its$std.error,
      its_slope_pval = b3_its$p.value,

      # Pre/post model results
      prepost_intercept = intercept_prepost$estimate,
      prepost_effect = effect_prepost$estimate,
      prepost_effect_se = effect_prepost$std.error,
      prepost_effect_pval = effect_prepost$p.value,
      prepost_ci_lower = prepost_effect - 1.96 * prepost_effect_se,
      prepost_ci_upper = prepost_effect + 1.96 * prepost_effect_se
    )
  }

  # map over all test dates
  results <- purrr::map_dfr(test_dates, ~fit_model_for_date(.x, data))

  return(results)
}

# run function
cohort_unwinding_tests_simple <- test_unwinding_dates_simple(
  data = cohort_filtered,
  outcome_var = "ce_after_12",
  baseline_start = as.Date("2020-01-01"),
  unwinding_test_start = as.Date("2021-01-01"),
  unwinding_test_end = as.Date("2023-04-08"),
  data_end_date = as.Date("2023-08-31")
)

# Write full results to Excel
library(openxlsx)
write.xlsx(cohort_unwinding_tests_simple, "event_study_results.xlsx")

# Plot ITS model results
p1 <- ggplot(cohort_unwinding_tests_simple, aes(x = unwinding_start_date, y = its_level_change)) +
  geom_ribbon(aes(ymin = its_level_ci_lower, ymax = its_level_ci_upper),
              alpha = 0.3) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.8) +
  labs(
    title = "ITS Model: Level Change (B2) by Unwinding Start Date",
    subtitle = "Model: Y = B0 + B1*t + B2*Post + B3*time_since_unwinding",
    x = "Unwinding Start Date",
    y = "B2: Level Change Coefficient"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10, color = "gray40"),
    axis.title = element_text(size = 11, face = "bold")
  )

# Plot pre/post model results
p2 <- ggplot(cohort_unwinding_tests_simple, aes(x = unwinding_start_date, y = prepost_effect)) +
  geom_ribbon(aes(ymin = prepost_ci_lower, ymax = prepost_ci_upper),
              alpha = 0.3) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.8) +
  labs(
    title = "Pre/Post Model: Effect by Unwinding Start Date",
    subtitle = "Model: Y = B0 + B1*Post (no time trends)",
    x = "Unwinding Start Date",
    y = "B1: Pre/Post Effect"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10, color = "gray40"),
    axis.title = element_text(size = 11, face = "bold")
  )

# Display both plots
library(patchwork)
p1 / p2

```

{{< pagebreak >}}

# Sensitivity Analyses

```{r}
# Table stuff
mk_tbl <- function(fit) {
  tbl_regression(
    fit,
    intercept    = TRUE,
    pvalue_fun   = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 3),
    conf.int     = FALSE
  ) |>
    add_significance_stars(hide_p = TRUE, pattern = "{estimate}{stars}") |>
    modify_column_hide(columns = c(std.error))
}

compare_models <- function(model_names, spanners) {
  tbls <- lapply(model_names, function(nm) mk_tbl(models[[nm]]))
  tbl_merge(tbls = tbls, tab_spanner = spanners)
}
```

## Diabetes Subgroup Exclude Pre-existing

### Graph

```{r}
# Diabetes screening graph

diab.subgroup %>%
  group_by(anchor_date_twoweeks, pre_existing_diab) %>%
  summarise(out_diab_screen_12 = mean(out_diab_screen_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_diab_screen_12, color=as.factor(pre_existing_diab))) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  labs(
    title = "Diabetes Screening Rates 12 Months (Pre-Existing Comparison)",
    x = "Date",
    y = "% Episode with Screening",
  ) +
  theme_minimal()
```

### Models

```{r}
# 1) Restricted data (exclude pre-existing diabetes)
diab.subgroup_nopre <- dplyr::filter(diab.subgroup, pre_existing_diab == 0)

# 2) Refit ONLY the restricted models, using the *exact same formulas* as originals
fml_unadj <- formula(models$diab_screen_unadj)
fml_adj   <- formula(models$diab_screen_adj)

models$diab_screen_unadj_nopre <- lm(fml_unadj, data = diab.subgroup_nopre)
models$diab_screen_adj_nopre   <- lm(fml_adj,   data = diab.subgroup_nopre)

```

### Diabetes Screening Unadjusted

```{r}
compare_models(
  c("diab_screen_unadj", "diab_screen_unadj_nopre"),
  c("Full Sample", "Excluding Pre-Existing Diabetes")
) |>
  as_flex_table() |>
  FitFlextableToPage()
```

### Diabetes Screening Adjusted

```{r}
compare_models(
  c("diab_screen_adj", "diab_screen_adj_nopre"),
  c("Full Sample", "Excluding Pre-Existing Diabetes")
) |>
  as_flex_table() |>
  FitFlextableToPage()
```

{{< pagebreak >}}

## Diabetes Subgroup Test Type Graphs

```{r}

# Summary
summary_time <- bind_rows(
  diab.subgroup %>%
    filter(!is.na(anchor_date_twoweeks)) %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(test = "HbA1c (12m)",
              rate = mean(out_diab_screen_hba1c_12, na.rm = TRUE),
              n = sum(!is.na(out_diab_screen_hba1c_12)),
              .groups = "drop"),
  diab.subgroup %>%
    filter(!is.na(anchor_date_twoweeks)) %>%
    group_by(anchor_date_twoweeks) %>%
    summarise(test = "GTT (12m)",
              rate = mean(out_diab_screen_gtt_12, na.rm = TRUE),
              n = sum(!is.na(out_diab_screen_gtt_12)),
              .groups = "drop")
)

ggplot(summary_time, aes(x = anchor_date_twoweeks, y = rate, color = test)) +
  geom_line(size=1) +
  scale_y_continuous(breaks = seq(0, 1, 0.1),
                     labels = function(x) paste0(round(100 * x), "%")) +
  labs(x = NULL, y = "12-month test rate",
       title = "12-month Screening Rates Over Time",
       color = NULL) +
  theme_minimal(base_size = 12)


```

{{< pagebreak >}}

### Diabetes Test Type Models

```{r}
# 1) derive RHS from your stored overall models (keeps Unwinding + interactions identical)
rhs_unadj <- paste(attr(terms(models$diab_screen_unadj), "term.labels"), collapse = " + ")
rhs_adj   <- paste(attr(terms(models$diab_screen_adj),   "term.labels"), collapse = " + ")

# 2) build formulas for test-type outcomes using that RHS
fml_hba1c_unadj <- as.formula(paste("out_diab_screen_hba1c_12 ~", rhs_unadj))
fml_hba1c_adj   <- as.formula(paste("out_diab_screen_hba1c_12 ~", rhs_adj))
fml_gtt_unadj   <- as.formula(paste("out_diab_screen_gtt_12 ~",   rhs_unadj))
fml_gtt_adj     <- as.formula(paste("out_diab_screen_gtt_12 ~",   rhs_adj))

# 3) fit ONCE and store (no refit of originals)
models$diab_hba1c_unadj <- lm(fml_hba1c_unadj, data = diab.subgroup)
models$diab_hba1c_adj   <- lm(fml_hba1c_adj,   data = diab.subgroup)
models$diab_gtt_unadj   <- lm(fml_gtt_unadj,   data = diab.subgroup)
models$diab_gtt_adj     <- lm(fml_gtt_adj,     data = diab.subgroup)

# 4) combined table using your helpers
nm  <- c("diab_screen_unadj","diab_screen_adj",
         "diab_hba1c_unadj","diab_hba1c_adj",
         "diab_gtt_unadj","diab_gtt_adj")
lbl <- c("Overall (Unadj)","Overall (Adj)",
         "HbA1c (Unadj)","HbA1c (Adj)",
         "GTT (Unadj)","GTT (Adj)")

compare_models(nm, lbl) |>
  as_flex_table() |>
  FitFlextableToPage()

```

{{< pagebreak >}}

## Excluding COVID

```{r}

exclude_start <- as.Date("2019-03-18")
exclude_end   <- as.Date("2020-04-17")
exclude_days  <- as.integer(exclude_end - exclude_start + 1L)
origin        <- as.Date("2019-01-01")

# helper: map a DATE -> reindexed (gap-removed) 0-based biweekly counter
date_to_reidx_biweek0 <- function(d) {
  # days since origin, minus the removed block if date is after the excluded window
  days_eff <- as.integer(d - origin) - ifelse(d > exclude_end, exclude_days, 0L)
  as.integer(days_eff / 14)
}

# reindexed intervention start times on the SAME gap-removed biweekly scale
ffcra_start_date    <- time_periods %>% dplyr::filter(period == "FFCRA") %>% dplyr::pull(start)
exposure_start_date <- time_periods %>% dplyr::filter(period == "Exposure_Unwinding") %>% dplyr::pull(start)

ffcra_start_t_reidx    <- date_to_reidx_biweek0(ffcra_start_date)
exposure_start_t_reidx <- date_to_reidx_biweek0(exposure_start_date)

diab.subgroup_excluded <- diab.subgroup %>%
  filter(!(anchor_date >= exclude_start & anchor_date <= exclude_end)) %>%
  mutate(
    # gap-removed 0-based time
    t = date_to_reidx_biweek0(anchor_date),

    # centered clocks (0 at intervention start)
    t_after_FFCRA    = pmax(0, t - ffcra_start_t_reidx),
    t_after_Exposure = pmax(0, t - exposure_start_t_reidx),

    # optional: keep a plotting date aligned with reindexed t
    anchor_date_twoweeks = origin + t * 14
  )

htn.subgroup_excluded <- htn.subgroup %>%
  filter(!(anchor_date >= exclude_start & anchor_date <= exclude_end)) %>%
  mutate(
    t = date_to_reidx_biweek0(anchor_date),
    t_after_FFCRA    = pmax(0, t - ffcra_start_t_reidx),
    t_after_Exposure = pmax(0, t - exposure_start_t_reidx),
    anchor_date_twoweeks = origin + t * 14
  )

# Get RHS (now based on UPDATED models that use t + centered clocks)
rhs_unadj_excl <- paste(attr(terms(models$diab_screen_unadj), "term.labels"), collapse = " + ")
rhs_adj_excl   <- paste(attr(terms(models$diab_screen_adj),   "term.labels"), collapse = " + ")

fit_excluded_reindexed <- function(base_label, outcome, data, adjusted = FALSE) {
  rhs <- if (adjusted) rhs_adj_excl else rhs_unadj_excl
  fml <- as.formula(paste(outcome, "~", rhs))
  nm  <- paste0(base_label, if (adjusted) "_adj_excluded_reidx" else "_unadj_excluded_reidx")
  models[[nm]] <<- lm(fml, data = data)
  nm
}

# Diabetes cohort
fit_excluded_reindexed("diab_screen",         "out_diab_screen_12",     diab.subgroup_excluded, adjusted = FALSE)
fit_excluded_reindexed("diab_screen",         "out_diab_screen_12",     diab.subgroup_excluded, adjusted = TRUE)
fit_excluded_reindexed("diab_any_outpatient", "out_any_outpatient_12",  diab.subgroup_excluded, adjusted = FALSE)
fit_excluded_reindexed("diab_any_outpatient", "out_any_outpatient_12",  diab.subgroup_excluded, adjusted = TRUE)

# HTN cohort
fit_excluded_reindexed("htn_med",             "out_htn_med_12",         htn.subgroup_excluded,  adjusted = FALSE)
fit_excluded_reindexed("htn_med",             "out_htn_med_12",         htn.subgroup_excluded,  adjusted = TRUE)
fit_excluded_reindexed("htn_any_outpatient",  "out_any_outpatient_12",  htn.subgroup_excluded,  adjusted = FALSE)
fit_excluded_reindexed("htn_any_outpatient",  "out_any_outpatient_12",  htn.subgroup_excluded,  adjusted = TRUE)


```

```{r}
compare_models(
  c("diab_screen_unadj", "diab_screen_unadj_excluded_reidx",
    "diab_screen_adj",   "diab_screen_adj_excluded_reidx"),
  c("Original - Unadj",  "Excluded COVID - Unadj",
    "Original - Adj",    "Excluded COVID - Adj")
) |> as_flex_table() |> FitFlextableToPage()

```

```{r}
compare_models(
  c("diab_any_outpatient_unadj", "diab_any_outpatient_unadj_excluded_reidx",
    "diab_any_outpatient_adj",   "diab_any_outpatient_adj_excluded_reidx"),
  c("Original - Unadj",          "Excluded COVID - Unadj",
    "Original - Adj",            "Excluded COVID - Adj")
) |> as_flex_table() |> FitFlextableToPage()


```

```{r}
compare_models(
  c("htn_med_unadj", "htn_med_unadj_excluded_reidx",
    "htn_med_adj",   "htn_med_adj_excluded_reidx"),
  c("Original - Unadj", "Excluded COVID - Unadj",
    "Original - Adj",   "Excluded COVID - Adj")
) |> as_flex_table() |> FitFlextableToPage()


```

```{r}
compare_models(
  c("htn_any_outpatient_unadj", "htn_any_outpatient_unadj_excluded_reidx",
    "htn_any_outpatient_adj",   "htn_any_outpatient_adj_excluded_reidx"),
  c("Original - Unadj",         "Excluded COVID - Unadj",
    "Original - Adj",           "Excluded COVID - Adj")
) |> as_flex_table() |> FitFlextableToPage()
```

{{< pagebreak >}}

# Other Break Analysis

```{r}
# Set Paths 
current.path <- here::here()
poem.path <- dirname(dirname(current.path))
codeset.path <- file.path(poem.path,"poem", "data","ancillary")

dshs.numbers.path <- file.path(codeset.path,"monthly-enrollment-by-risk-group.xlsx")

dshs.numbers <- read_excel(dshs.numbers.path, skip = 2) %>% 
  clean_names()

dshs.numbers <- 
dshs.numbers %>%
   mutate(
    date_col = suppressWarnings(as.numeric(month)),  
    month = as.Date(date_col, origin = "1899-12-30") 
  )

dshs.numbers <- 
dshs.numbers %>%
  filter(month > as.Date("2019-01-01"))


```

## Percent Change in DSHS Numbers

```{r}
dshs.numbers.change <- 
 dshs.numbers %>%
  arrange(month) %>% 
  mutate(
    pct_change_pregnant = (pregnant_women / lag(pregnant_women) - 1) * 100
  ) 


dshs.numbers.change %>%
  ggplot(aes(x = month, y = pct_change_pregnant)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    title = "Month-to-Month Percent Change in Pregnant Women Enrollment (From DSHS numbers)",
    x = "Month",
    y = "Percent Change (%)"
  ) +
  theme_minimal()


```

```{r}
dshs.numbers.change %>%
  filter(month >= as.Date("2023-01-01") & month <= as.Date("2024-06-30")) %>%
  select(month, pregnant_women, pct_change_pregnant) %>%
  mutate(
    pregnant_women = round(pregnant_women, 0),
    pct_change_pregnant = round(pct_change_pregnant, 2)
  ) %>%
  flextable() %>%
  set_header_labels(
    month = "Month",
    pregnant_women = "Pregnant Women (Count)",
    pct_change_pregnant = "Percent Change (%)"
  ) %>%
  colformat_num(j = "pct_change_pregnant", suffix = "%") %>%
  theme_box() %>%
  autofit() %>%
  align(align = "center", part = "all") %>%
  bold(part = "header") %>%
  set_caption("Month-to-Month Percent Change in Pregnant Women Enrollment (Jan 2023 - Jun 2024)")

```

## Change in CE (from cohort)

```{r}
ce.change <-
cohort %>%
  filter(anchor_date_month > as.Date("2019-12-31")) %>%
  group_by(anchor_date_month) %>%
  summarize(pct_ce_after_12 = mean(ce_after_12), .groups = "drop") %>%
  arrange(anchor_date_month) %>% 
  mutate(
    pct_change_pregnant = (pct_ce_after_12 / lag(pct_ce_after_12) - 1) * 100
  ) 

ce.change %>%
  ggplot(aes(x = anchor_date_month, y = pct_change_pregnant)) +
  geom_line(size = 1) +
  geom_point() +
  labs(
    title = "Month-to-Month Percent Change in Pregnant Women Enrollment (From DSHS numbers)",
    x = "Month",
    y = "Percent Change (%)"
  ) +
  theme_minimal()

```

```{r}
ce_tbl <- ce.change %>%
   filter(anchor_date_month >= as.Date("2022-01-01") & anchor_date_month <= as.Date("2023-09-30")) %>%
  mutate(
    rate_pct = pct_ce_after_12 * 100,                 # level as %
    mom_change_pct = pct_change_pregnant              # already in %
  ) %>%
  select(anchor_date_month, rate_pct, mom_change_pct) %>%
  mutate(
    rate_pct = round(rate_pct, 2),
    mom_change_pct = round(mom_change_pct, 2)
  )

# Flextable
ce_tbl %>%
  flextable() %>%
  set_header_labels(
    anchor_date_month = "Month",
    rate_pct = "CE After 12 (Level, %)",
    mom_change_pct = "MoM Change (%)"
  ) %>%
  colformat_num(j = "rate_pct", suffix = "%") %>%
  colformat_num(j = "mom_change_pct", suffix = "%") %>%
  theme_box() %>%
  autofit() %>%
  align(align = "center", part = "all") %>%
  bold(part = "header") %>%
  set_caption("Monthly CE After 12 Rate and Month-over-Month Change")
```

# Scratch (check predicted values)

```{r}
# Function to plot ITS model fit vs raw data (UPDATED for centered clocks)
plot_its_model <- function(model, data, outcome_var, title = NULL) {

  # Raw means by time point (t)
  raw_means <- data %>%
    group_by(t, period_FFCRA, period_Exposure_Unwinding) %>%
    summarise(
      raw_mean = mean(.data[[outcome_var]], na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      period = case_when(
        period_Exposure_Unwinding == 1 ~ "Unwinding",
        period_FFCRA == 1 ~ "FFCRA",
        TRUE ~ "Baseline"
      )
    )

  # Prediction grid = observed combinations of the RHS variables
  pred_data <- data %>%
    select(t, period_FFCRA, period_Exposure_Unwinding, t_after_FFCRA, t_after_Exposure) %>%
    distinct() %>%
    mutate(
      period = case_when(
        period_Exposure_Unwinding == 1 ~ "Unwinding",
        period_FFCRA == 1 ~ "FFCRA",
        TRUE ~ "Baseline"
      )
    )

  # Add covariate means if they exist in the model
  if ("age" %in% names(coef(model))) {
    pred_data$age <- mean(data$age, na.rm = TRUE)
  }
  if ("no_transfusion_weight" %in% names(coef(model))) {
    pred_data$no_transfusion_weight <- mean(data$no_transfusion_weight, na.rm = TRUE)
  }

  # Get predictions
  pred_data$fitted <- predict(model, newdata = pred_data)

  # Create the plot
  p <- ggplot() +
    # Raw data points
    geom_point(
      data = raw_means,
      aes(x = t, y = raw_mean, color = period),
      alpha = 0.6, size = 2.5
    ) +
    # Fitted lines
    geom_line(
      data = pred_data %>% arrange(t),
      aes(x = t, y = fitted, color = period),
      linewidth = 1.2
    ) +
    scale_color_manual(values = c(
      "Baseline"  = "#1f77b4",
      "FFCRA"     = "#ff7f0e",
      "Unwinding" = "#2ca02c"
    )) +
    labs(
      title = title %||% paste("ITS Model Fit:", outcome_var),
      x = "Biweekly time (t, 0-based)",
      y = outcome_var,
      color = "Period"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      panel.grid.minor = element_blank()
    )

  return(p)
}

# Plot diabetes screening adjusted model
plot_its_model(
  model = models$diab_screen_adj,
  data = diab.subgroup,
  outcome_var = "out_diab_screen_12",
  title = "Diabetes Screening (Adjusted)"
)



```
