---
title: "POEM TX Paper 1"
date: today
format: 
  docx:
    df-print: paged
    page-layout: full
    fig-width: 12
    fig-height: 8
    out-width: 100%
  html:
    fig-width: 12
    fig-height: 8
editor: visual
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r setup}
#| echo: false
#| warning: false
#| 

# Load packages 
pacman::p_load(RPostgres, DBI, keyring, janitor, tidyverse, readxl,
               gtsummary, ggplot2, labelled, clipr, viridis, ggrepel, scales, ggthemes, flextable, DiagrammeR,
               odbc, openxlsx, beepr, tictoc, here, sandwich, lmtest, lubridate, patchwork, ggnewscale, cowplot)

#### Setup File Paths ####
# Get the location of this current .R file 
current_dir <- here::here()

#### Database Connection 
spc <- dbConnect(odbc::odbc(),
	 dsn = "SPC",
	 bigint = "integer")

options(scipen = 999)


# Set Themes

my_theme <- function() {
  theme_minimal(base_size = 10) +
    theme(
      text = element_text(family = "sans", size=14),
      axis.text.y = element_text(size = 12, face="plain", margin = margin(r = 10, unit = "pt")),
      axis.title.y = element_text(size = 13, face = "bold", margin = margin(r = 20, unit = "pt")) ,
      axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 20, unit = "pt")) , 
      plot.caption = element_text(size = 12, face = "italic", margin = margin(t = 20, r=20, b = 5, l=20, unit = "pt"))
    )
}

set_flextable_defaults(padding=2.5)

theme_set(my_theme())

FitFlextableToPage <- function(ft, pgwidth = 6.5){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}


```

```{r get-outcomes}

all.df <- dbGetQuery(spc, " 
  select * from chcdwork.dbo.poem_cohort_analysis1 
 ;")

all.df[sapply(all.df, is.numeric)] <- 
  lapply(all.df[sapply(all.df, is.numeric)], function(x) ifelse(is.na(x), 0, x))

```

```{r clean-data}
# Grab Data 

episodes <- 
  all.df %>%
  mutate(
    hispanic = case_when(
      race_cd == 3 ~ 1,
      TRUE ~ 0
    )
  ) %>% mutate(
    race_desc = case_when(
      race_cd == 1 ~ "White, non-Hispanic",
      race_cd == 2 ~ "Black, non-Hispanic",
      race_cd == 3 ~ "Hispanic",
      race_cd == 4 ~ "American Indian or Alaskan",
      race_cd == 5 ~ "Asian, Pacific Islander",
      race_cd == 6 ~ "Unknown/Other",
      TRUE ~  "Unknown/Other"
    ),
    me_desc = case_when(
      me_code == "B" ~ "Pregnancy",
      me_code == "C" ~ "Emergency",
      me_code == "D" ~ "Other",
      me_code == "F" ~ "Other",
      me_code == "I" ~ "Institutional regular (CATS 1 3 or 4) (BP16 or 17)",
      me_code == "N" ~ "FFCHE (Former Foster Child in Higher Education)",
      me_code == "P" ~ "Three months prior",
      me_code == "Q" ~ "QMD coverage (Medicare only)",
      me_code == "R" ~ "Regular",
      me_code == "T" ~ "1929(b) Base plan 20 MAO client",
      me_code == "W" ~ "Healthy Texas Women",
      TRUE ~ "Unknown"
    ),
    preg_med = case_when(
  me_code == "R" ~ 1,
  me_code == "C" ~ 0,
  TRUE ~ NA_real_
),
    age_group = case_when(
    age <= 18 ~ "0-18",
    age >= 19 & age <= 24 ~ "19-24",
    age >= 25 & age <= 34 ~ "25-34",
    age >= 35 & age <= 44 ~ "35-44",
    age >= 45 & age <= 55 ~ "45-55",
    TRUE ~ NA_character_
  ),
     state_tx = case_when(
      state == "TX" ~ "TX",
      state != "TX" ~ "Non-TX",
      TRUE ~ "Unknown"
    )
  ) %>%
  mutate(los_less_60 = case_when(
    los <= 60 ~ 1,
    TRUE ~ 0
  )) %>%
  mutate(monthly_anchor_date = as.Date(format(anchor_date, "%Y-%m-01")))

var_label(episodes) <- list(
    anchor_year = "Year",
    age = "Age",
    race_desc = "Race/Ethnicity",
    age_group = "Age Group",
    me_desc = "Enrollment Category (Month of birth episode)",
    state_tx = "State (Month of birth episode)",
    outcome_type = "Birth Outcome",
    los = "Length of Stay",
    hispanic = "Hispanic",
    los_less_60 = "LOS <= 60 days",
    diab_sample = "Diabetes Sample",
    htn_sample = "HTN Sample",
    monthly_anchor_date = "Anchor Month",
    smm_weight = "Index SMM Weight",
    no_transfusion_weight = "Index No Transfusion Weight",
    urban = "Urban"
  )


```

```{r}
cohort <- 
episodes %>% 
  filter(age >= 19 & age <= 55) %>%
  filter(enrolled_birth == 1) %>%
  filter(state_tx == 'TX') %>% 
  filter(los <= 60) %>%
  filter( me_code == "R")
  
```

```{r add-time-vars}
cohort <- 
cohort %>%
  mutate(
    week_counter = as.integer(difftime(anchor_date, as.Date('2019-01-01'), units = "weeks")) + 1,
    biweekly_counter = as.integer(difftime(anchor_date, as.Date('2019-01-01'), units = "days") / 14) + 1,
    monthly_counter = as.integer(difftime(anchor_date, as.Date('2019-01-01'), units = "days") / 30) + 1,
    anchor_date_week = as.Date('2019-01-01') + (week_counter - 1) * 7,
    anchor_date_twoweeks = as.Date('2019-01-01') + (biweekly_counter - 1) * 14,
    anchor_date_month = as.Date('2019-01-01') + (monthly_counter - 1) * 30
  )


# # Updated time periods
# time_periods.6months <- list(
#   pre_FFCRA = list(start = as.Date('2019-01-01'), end = as.Date('2019-09-18')),
#   COVID = list(start = as.Date('2019-09-19'), end = as.Date('2020-04-17')),
#   FFCRA = list(start = as.Date('2020-04-18'), end = as.Date('2022-09-30'))
#   # , Unwinding = list(start = as.Date('2022-10-01'), end = as.Date('2023-08-31'))
#   # Postpartum_extension = list(start = as.Date('2023-09-01'), end = as.Date('2024-06-30'))
# )

time_periods.6months <- tibble::tibble(
  period = factor(c("pre_FFCRA", "COVID", "FFCRA"), levels = c("pre_FFCRA", "COVID", "FFCRA")),
  start = as.Date(c("2019-01-01", "2019-09-19", "2020-04-18")),
  end   = as.Date(c("2019-09-18", "2020-04-17", "2022-09-30"))
)

# For sensitibity analyses
time_periods.6months.old <- tibble::tibble(
  period = factor(c("pre_FFCRA", "COVID", "FFCRA"), levels = c("pre_FFCRA", "COVID", "FFCRA")),
  start = as.Date(c("2019-01-01", "2019-09-19", "2020-07-01")),
  end   = as.Date(c("2019-09-18", "2020-06-30", "2022-09-30"))
)



# Get a date six months before end of FY23
six_months_before <- as.Date("2023-08-31") %m-% months(6)
twelve_months_before <- as.Date("2023-08-31") %m-% months(12)


cohort <- cohort %>%
  mutate(
    period_COVID = case_when(
      anchor_date >= time_periods.6months %>% filter(period == "COVID") %>% pull(start) &
      anchor_date <= time_periods.6months %>% filter(period == "COVID") %>% pull(end) ~ 1,
      TRUE ~ 0
    ),
    period_FFCRA = case_when(
      anchor_date >= time_periods.6months %>% filter(period == "FFCRA") %>% pull(start) &
      anchor_date <= time_periods.6months %>% filter(period == "FFCRA") %>% pull(end) ~ 1,
      TRUE ~ 0
    )
    # ,
    # period_Unwinding = case_when(
    #   anchor_date >= time_periods.6months %>% filter(period == "Unwinding") %>% pull(start) &
    #   anchor_date <= time_periods.6months %>% filter(period == "Unwinding") %>% pull(end) ~ 1,
    #   TRUE ~ 0
    # ),
    # period_Postpartum_extension = case_when(
    #   anchor_date >= time_periods.6months %>% filter(period == "Postpartum_extension") %>% pull(start) &
    #   anchor_date <= time_periods.6months %>% filter(period == "Postpartum_extension") %>% pull(end) ~ 1,
    #   TRUE ~ 0
    # )
  )



```

This is after restricting enrollment to "Regular" using the me_code variable.

# Table 1

```{r}
sub.cohort <- 
cohort %>% filter(htn_sample==1 | diab_sample==1)  %>%
  filter(anchor_date <= twelve_months_before)
```

```{r}
# Make long version
long_subcohort <- sub.cohort %>%
  mutate(id = row_number()) %>%
  pivot_longer(cols = c(htn_sample, diab_sample), 
               names_to = "group", 
               values_to = "in_group") %>%
  filter(in_group == 1)

# Table by group 
table_by_group <- long_subcohort %>%
  mutate(group = recode(group,
                        htn_sample = "Hypertension",
                        diab_sample = "Diabetes")) %>%
  select(group, outcome_type, anchor_year, race_desc, age_group, hispanic, smm_weight, no_transfusion_weight) %>%
  tbl_summary(by = group)

# Overall
table_overall <- sub.cohort %>%
  select(outcome_type, anchor_year, race_desc, age_group, hispanic, smm_weight, no_transfusion_weight) %>%
  tbl_summary()

# Merge 
merged_table <- tbl_merge(
  tbls = list(table_overall, table_by_group),
  tab_spanner = c("**Overall**", "**By Condition**")
)


merged_table %>%
  as_flex_table() %>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  autofit() %>%
  FitFlextableToPage()

```

{{< pagebreak >}}

# Outcomes

```{r}
htn.subgroup <- 
  cohort %>% filter(htn_sample==1) %>%
  filter(anchor_date <= twelve_months_before)
```

```{r}
diab.subgroup <- 
  cohort %>% 
  filter(diab_sample==1) %>%
  filter(anchor_date <= twelve_months_before)
```

## Graphs

```{r}

# Get period starts
period_starts <- time_periods.6months %>%
  select(date = start, period) %>%
  arrange(date) %>%
  mutate(period = factor(period, levels = period))

# Diabetes screening graph
diab.screening <- 
diab.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_diab_screen_12 = mean(out_diab_screen_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_diab_screen_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Diabetes Screening Rates 12 Months",
    x = "Date",
    y = "% Episode with Screening",
    color = "Period Start"
  ) +
  theme_minimal()

# Diabetes Visit graph
diab.visit <- 
diab.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_postpartum_12 = mean(out_postpartum_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_postpartum_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Diabetes Subgroup Postpartum Visit 12 Months",
    x = "Date",
    y = "% Episodes with visit",
    color = "Period Start"
  ) +
  theme_minimal()

# HTN Visit graph
htn.visit <- 
htn.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_postpartum_12 = mean(out_postpartum_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_postpartum_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Hypertension Subgroup Postpartum Visit 12 Months",
    x = "Date",
    y = "% Episodes with visit",
    color = "Period Start"
  ) +
  theme_minimal()


htn.med <- 
htn.subgroup %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(out_htn_med_12 = mean(out_htn_med_12)) %>%
  ggplot(aes(x = anchor_date_twoweeks, y = out_htn_med_12)) +
  geom_line(linewidth = 1) +
  geom_vline(
    data = period_starts,
    aes(xintercept = date, color = period),
    linetype = "dashed",
    linewidth=.75
  ) +
  scale_y_continuous(labels = percent, limits = c(0, 1)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Hypertension Subgroup Medication 12 Months",
    x = "Date",
    y = "% Episodes with medication",
    color = "Period Start"
  ) +
  theme_minimal()



# Combine 
combined_plot <- (
  (diab.screening + diab.visit) /
  (htn.visit + htn.med)
) +
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")

combined_plot

```

{{< pagebreak >}}

# Outpatient

## Share of Categories

This is based on the chart in the appendix we got the categories from

```{r}
op.sum <- 
dbGetQuery(spc, " 
  select * from CHCDWORK.dbo.poem_outcomes_outpatient_categories_summary 
 ;")


op.sum %>% arrange(desc(share_of_visits)) %>% flextable()%>%
  theme_box() %>%
  padding(padding = 1.5) %>%
  autofit() %>%
  FitFlextableToPage()
```

{{< pagebreak >}}

## % Who had any visit (0/1 Indicator)

```{r}
period_rects <- time_periods.6months %>%
  select(start, end, period)

visit.plots.y.n <- 
sub.cohort %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(
    PE = mean(out_pe_12, na.rm = TRUE),
    Preventive = mean(out_prev_12, na.rm = TRUE),
    Contraceptive = mean(out_contr_12, na.rm = TRUE),
    Mental_Health = mean(out_mental_12, na.rm = TRUE),
    Other = mean(out_other_12, na.rm = TRUE),
    Any_Outpatient = mean(out_any_outpatient_12, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  pivot_longer(
    cols = c(PE, Preventive, Contraceptive, Mental_Health, Other, Any_Outpatient),
    names_to = "visit_type",
    values_to = "percentage"
  ) %>%
  mutate(
    visit_type = factor(
      visit_type,
      levels = c("Any_Outpatient", "PE", "Preventive", "Contraceptive", "Mental_Health", "Other"),
      labels = c("Any Outpatient", "Postpartum Evaluation", "Preventive", "Contraceptive", "Mental Health", "Other")
    )
  ) 

ggplot() +
  geom_rect(
    data = period_rects,
    aes(xmin = start, xmax = end, ymin = 0, ymax = 1, fill = period),
    alpha = 0.2
  ) +
  geom_line(
    data = visit.plots.y.n,
    aes(x = anchor_date_twoweeks, y = percentage, color = visit_type),
    linewidth = 1
  ) +
  scale_fill_manual(
    name = "Time Period",
    values = c(
      "pre_FFCRA" = "#1B9E77",
      "COVID" = "#D95F02",
      "FFCRA" = "#7570B3"
    )
  ) +
  scale_color_manual(
    name = "Visit Type",
    values = c(
      "Any Outpatient" = "black",
      "Postpartum Evaluation" = "#E31A1C",
      "Preventive" = "#1F78B4",
      "Contraceptive" = "#33A02C",
      "Mental Health" = "#FF7F00",
      "Other" = "#6A3D9A"
    )
  ) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  labs(
    title = "Outpatient Visit Types - 12 Months Post-Delivery",
    x = "Date",
    y = "% Episodes with Visits"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")


```

## Average Visits per Person

```{r}
visit_plot <- sub.cohort %>%
  group_by(anchor_date_twoweeks) %>%
  summarise(
    PE = mean(pe_visit_days_12, na.rm = TRUE),
    Preventive = mean(prev_visit_days_12, na.rm = TRUE),
    Contraceptive = mean(contr_visit_days_12, na.rm = TRUE),
    Mental_Health = mean(mental_visit_days_12, na.rm = TRUE),
    Other = mean(other_visit_days_12, na.rm = TRUE),
    Any_Outpatient = mean(total_visit_days_12, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  pivot_longer(
    cols = c(PE, Preventive, Contraceptive, Mental_Health, Other, Any_Outpatient),
    names_to = "visit_type",
    values_to = "avg_visits"
  ) %>%
  mutate(
    visit_type = factor(
      visit_type,
      levels = c("Any_Outpatient", "PE", "Preventive", "Contraceptive", "Mental_Health", "Other"),
      labels = c("Any Outpatient", "Postpartum Evaluation", "Preventive", "Contraceptive", "Mental Health", "Other")
    )
  ) 

ggplot() +
  geom_rect(
    data = period_rects,
    aes(xmin = start, xmax = end, ymin = 0, ymax = Inf, fill = period),
    alpha = 0.2
  ) +
  geom_line(
    data = visit_plot,
    aes(x = anchor_date_twoweeks, y = avg_visits, color = visit_type),
    linewidth = 1
  ) +
  scale_fill_manual(
    name = "Time Period",
    values = c(
      "pre_FFCRA" = "#1B9E77",
      "COVID" = "#D95F02",
      "FFCRA" = "#7570B3"
    )
  ) +
  scale_color_manual(
    name = "Visit Type",
    values = c(
      "Any Outpatient" = "black",
      "Postpartum Evaluation" = "#E31A1C",
      "Preventive" = "#1F78B4",
      "Contraceptive" = "#33A02C",
      "Mental Health" = "#FF7F00",
      "Other" = "#6A3D9A"
    )
  ) +
  labs(
    title = "Outpatient Visit Types - Avg Number of Visits (12 Months Post-Delivery)",
    x = "Date",
    y = "Average Number of Visits"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

{{< pagebreak >}}

# Regression Models

## Diabetes Screening

Unadjusted

```{r}
lm(out_diab_screen_12 ~  biweekly_counter + period_COVID + period_FFCRA  +
                         biweekly_counter*period_COVID + biweekly_counter*period_FFCRA 
     ,   data=diab.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

Adjusted

```{r}

lm(out_diab_screen_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                       biweekly_counter*period_COVID + biweekly_counter*period_FFCRA + 
                       age + no_transfusion_weight
     ,   data=diab.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

{{< pagebreak >}}

## Diabetes Postpartum Visits

Unadjusted

```{r}
lm(out_postpartum_12 ~    biweekly_counter + period_COVID + period_FFCRA + 
                         biweekly_counter*period_COVID + biweekly_counter*period_FFCRA
     ,   data=diab.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

Adjusted

```{r}

lm(out_postpartum_12 ~ biweekly_counter + period_COVID + period_FFCRA + 
                       biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  + 
                       age + no_transfusion_weight
     ,   data=diab.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

{{< pagebreak >}}

## HTN Medication

Unadjusted

```{r}
lm(out_htn_med_12 ~   biweekly_counter + period_COVID + period_FFCRA +
                         biweekly_counter*period_COVID + biweekly_counter*period_FFCRA 
     ,   data=htn.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

Adjusted

```{r}

lm(out_htn_med_12 ~  biweekly_counter + period_COVID + period_FFCRA + 
                       biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  + 
                       age + no_transfusion_weight
     ,   data= htn.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 
```

{{< pagebreak >}}

## HTN Postpartum Visits

Unadjusted

```{r}
lm(out_postpartum_12 ~   biweekly_counter + period_COVID + period_FFCRA + 
                         biweekly_counter*period_COVID + biweekly_counter*period_FFCRA 
     ,   data=htn.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

Adjusted

```{r}

lm(out_postpartum_12 ~  biweekly_counter + period_COVID + period_FFCRA + 
                       biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  + 
                       age + no_transfusion_weight
     ,   data= htn.subgroup ) %>%
  tbl_regression(.,
  intercept = TRUE,
  pvalue_fun = ~ style_pvalue(.x, digits = 2),
  estimate_fun = ~ style_number(.x, digits = 4)
) 

```

{{< pagebreak >}}

# Sensitivity Analyses

## Time Periods

```{r}
cohort_alt <- cohort %>%
  filter(anchor_date <= twelve_months_before)

# # Reapply period definitions with the same variable names (no _alt suffix)
# cohort_alt <- cohort_alt %>%
#   mutate(
#     # Overwrite the original period variables with alternative definitions
#     period_COVID = case_when(
#       anchor_date >= time_periods.6months.old$COVID$start & 
#       anchor_date <= time_periods.6months.old$COVID$end ~ 1,
#       TRUE ~ 0
#     ),
#     period_FFCRA = case_when(
#       anchor_date >= time_periods.6months.old$FFCRA$start & 
#       anchor_date <= time_periods.6months.old$FFCRA$end ~ 1,
#       TRUE ~ 0
#     ),
#     period_Unwinding = case_when(
#       anchor_date >= time_periods.6months.old$Unwinding$start & 
#       anchor_date <= time_periods.6months.old$Unwinding$end ~ 1,
#       TRUE ~ 0
#     )
#   )


cohort_alt <- cohort_alt %>%
  mutate(
    period_COVID = case_when(
      anchor_date >= time_periods.6months.old %>% filter(period == "COVID") %>% pull(start) &
      anchor_date <= time_periods.6months.old %>% filter(period == "COVID") %>% pull(end) ~ 1,
      TRUE ~ 0
    ),
    period_FFCRA = case_when(
      anchor_date >= time_periods.6months.old %>% filter(period == "FFCRA") %>% pull(start) &
      anchor_date <= time_periods.6months.old %>% filter(period == "FFCRA") %>% pull(end) ~ 1,
      TRUE ~ 0
    )
    # ,
    # period_Unwinding = case_when(
    #   anchor_date >= time_periods.6months.old %>% filter(period == "Unwinding") %>% pull(start) &
    #   anchor_date <= time_periods.6months.old %>% filter(period == "Unwinding") %>% pull(end) ~ 1,
    #   TRUE ~ 0
    # )
  )


# Create subgroup datasets
diab.subgroup_alt <- cohort_alt %>% filter(diab_sample == 1)
htn.subgroup_alt <- cohort_alt %>% filter(htn_sample == 1)
```

```{r}
# Function to run and compare models 
run_comparison_models <- function(outcome_var, original_data, alt_data, model_title) {
  # Common formula for both original and alternative
  formula_unadj <- paste0(outcome_var, " ~ biweekly_counter + period_COVID + period_FFCRA + ",
                         "biweekly_counter*period_COVID + biweekly_counter*period_FFCRA ")
  
  formula_adj <- paste0(formula_unadj, " + age + no_transfusion_weight")
  
  # Original time periods models
  model_orig_unadj <- lm(as.formula(formula_unadj), data = original_data)
  model_orig_adj <- lm(as.formula(formula_adj), data = original_data)
  
  # Alternative time periods models
  model_alt_unadj <- lm(as.formula(formula_unadj), data = alt_data)
  model_alt_adj <- lm(as.formula(formula_adj), data = alt_data)
  
  tbl_orig_unadj <- tbl_regression(model_orig_unadj, intercept = TRUE, 
                                 pvalue_fun = function(x) style_pvalue(x, digits = 3),
                                 estimate_fun = ~ style_number(.x, digits = 3),
                                 conf.int = FALSE) %>%  # Remove CI
                   add_significance_stars(hide_p = TRUE, 
                                      pattern = "{estimate}{stars}") %>%
                   modify_column_hide(std.error)  # Hide standard errors
  
  tbl_orig_adj <- tbl_regression(model_orig_adj, intercept = TRUE, 
                               pvalue_fun = function(x) style_pvalue(x, digits = 3),
                               estimate_fun = ~ style_number(.x, digits = 3),
                               conf.int = FALSE) %>%  # Remove CI
                 add_significance_stars(hide_p = TRUE, 
                                    pattern = "{estimate}{stars}") %>%
                 modify_column_hide(std.error)  # Hide standard errors
  
  tbl_alt_unadj <- tbl_regression(model_alt_unadj, intercept = TRUE, 
                                pvalue_fun = function(x) style_pvalue(x, digits = 3),
                                estimate_fun = ~ style_number(.x, digits = 3),
                                conf.int = FALSE) %>%  # Remove CI
                  add_significance_stars(hide_p = TRUE, 
                                     pattern = "{estimate}{stars}") %>%
                  modify_column_hide(std.error)  # Hide standard errors
  
  tbl_alt_adj <- tbl_regression(model_alt_adj, intercept = TRUE, 
                              pvalue_fun = function(x) style_pvalue(x, digits = 3),
                              estimate_fun = ~ style_number(.x, digits = 3),
                              conf.int = FALSE) %>%  # Remove CI
                add_significance_stars(hide_p = TRUE, 
                                   pattern = "{estimate}{stars}") %>%
                modify_column_hide(std.error)  # Hide standard errors
  
  # Merge tables 
  tbl_merge(
    tbls = list(tbl_orig_unadj, tbl_alt_unadj, tbl_orig_adj, tbl_alt_adj),
    tab_spanner = c("Original - Unadj", "Alternative - Unadj", 
                    "Original - Adj", "Alternative - Adj")
  ) 
}
```

### Diabetes Screening (6-month)

```{r}
run_comparison_models("out_diab_screen_12", diab.subgroup, diab.subgroup_alt, 
                    "Diabetes Screening (12-month)") %>% as_flex_table() %>% FitFlextableToPage()
```

{{< pagebreak >}}

### Diabetes Postpartum Visits (6-month)

```{r}
run_comparison_models("out_postpartum_12", diab.subgroup, diab.subgroup_alt, 
                     "Diabetes Postpartum Visits (12-month)")%>% as_flex_table() %>% FitFlextableToPage()
```

{{< pagebreak >}}

### HTN Medication (6-month)

```{r}
run_comparison_models("out_htn_med_12", htn.subgroup, htn.subgroup_alt, 
                     "HTN Medication (12-month)")%>% as_flex_table() %>% FitFlextableToPage()
```

{{< pagebreak >}}

### HTN Postpartum Visits (6-month)

```{r}
run_comparison_models("out_postpartum_12", htn.subgroup, htn.subgroup_alt, 
                     "HTN Postpartum Visits (12-month)")%>% as_flex_table() %>% FitFlextableToPage()
```

{{< pagebreak >}}

## Diabetes Subgroup Test Type Graphs

```{r}
diab.breakdown.raw <- dbGetQuery(spc, " 
  select * from chcdwork.dbo.poem_cohort_analysis_diab_detail;
 ;")

diab.breakdown <- 
diab.breakdown.raw %>%
  mutate(
     state_tx = case_when(
      state == "TX" ~ "TX",
      state != "TX" ~ "Non-TX",
      TRUE ~ "Unknown"
    )
  ) %>%
  mutate(los_less_60 = case_when(
    los <= 60 ~ 1,
    TRUE ~ 0
  )) %>%
  mutate(monthly_anchor_date = as.Date(format(anchor_date, "%Y-%m-01"))) %>% 
  filter(age >= 19 & age <= 55) %>%
  filter(enrolled_birth == 1) %>%
  filter(state_tx == 'TX') %>% 
  filter(los <= 60) %>% 
  filter(diab_sample==1)


# For the 6-month outcome
diab.breakdown %>%
  group_by(monthly_anchor_date) %>%
  mutate(total_n = n()) %>%  # Calculate overall n for each monthly_anchor_date
  ungroup() %>%
  group_by(monthly_anchor_date, test_type) %>%
  filter(out_diab_screen_6 == 1) %>%
  summarise(
    n = n(),
    proportion = n / unique(total_n)  # Calculate the proportion
  ) %>%
  ggplot(aes(x = monthly_anchor_date, y = proportion, color = test_type)) +
  geom_line(linewidth = 1) +
  labs(
    title = "Proportion of Test Types (6-month Outcome)",
    y = "Proportion",
    x = "Monthly Anchor Date",
    color = "Test Type"
  ) + 
  scale_y_continuous(labels = percent, limits = c(0,1)) 


```

## Diabetes Test Type Models

### HbA1c Testing - Unadjusted

```{r}
# Unadjusted model for HbA1c
lm(out_diab_screen_hba1c_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                            biweekly_counter*period_COVID + biweekly_counter*period_FFCRA ,
   data = diab.subgroup) %>%
  tbl_regression(.,
                intercept = TRUE,
                pvalue_fun = ~ style_pvalue(.x, digits = 2),
                estimate_fun = ~ style_number(.x, digits = 4)) %>%
  add_global_p() %>%
  modify_header(label = "**HbA1c Test (6-month) - Unadjusted**")
```

### HbA1c Testing - Adjusted

```{r}
# Adjusted model for HbA1c
lm(out_diab_screen_hba1c_12 ~ biweekly_counter + period_COVID + period_FFCRA  +
                            biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  +
                            age + no_transfusion_weight,
   data = diab.subgroup) %>%
  tbl_regression(.,
                intercept = TRUE,
                pvalue_fun = ~ style_pvalue(.x, digits = 2),
                estimate_fun = ~ style_number(.x, digits = 4)) %>%
  add_global_p() %>%
  modify_header(label = "**HbA1c Test (6-month) - Adjusted**")
```

### GTT Testing - Unadjusted

```{r}
# Unadjusted model for GTT
lm(out_diab_screen_gtt_12 ~ biweekly_counter + period_COVID + period_FFCRA + 
                          biweekly_counter*period_COVID + biweekly_counter*period_FFCRA ,
   data = diab.subgroup) %>%
  tbl_regression(.,
                intercept = TRUE,
                pvalue_fun = ~ style_pvalue(.x, digits = 2),
                estimate_fun = ~ style_number(.x, digits = 4)) %>%
  add_global_p() %>%
  modify_header(label = "**GTT Test (6-month) - Unadjusted**")
```

### GTT Testing - Adjusted

```{r}
# Adjusted model for GTT
lm(out_diab_screen_gtt_12 ~ biweekly_counter + period_COVID + period_FFCRA + 
                          biweekly_counter*period_COVID + biweekly_counter*period_FFCRA +
                          age + no_transfusion_weight,
   data = diab.subgroup) %>%
  tbl_regression(.,
                intercept = TRUE,
                pvalue_fun = ~ style_pvalue(.x, digits = 2),
                estimate_fun = ~ style_number(.x, digits = 4)) %>%
  add_global_p() %>%
  modify_header(label = "**GTT Test (6-month) - Adjusted**")
```

{{< pagebreak >}}

## Combined Table Comparing All Models

```{r}
# Create list of models
models_list <- list(
  "Overall (Unadj)" = lm(out_diab_screen_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                             biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  ,
                           data = diab.subgroup),
  
  "Overall (Adj)" = lm(out_diab_screen_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                           biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  +
                           age + no_transfusion_weight,
                         data = diab.subgroup),
  
  "HbA1c (Unadj)" = lm(out_diab_screen_hba1c_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                           biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  ,
                         data = diab.subgroup),
  
  "HbA1c (Adj)" = lm(out_diab_screen_hba1c_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                         biweekly_counter*period_COVID + biweekly_counter*period_FFCRA +  
                         age + no_transfusion_weight,
                       data = diab.subgroup),
  
  "GTT (Unadj)" = lm(out_diab_screen_gtt_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                         biweekly_counter*period_COVID + biweekly_counter*period_FFCRA  ,
                       data = diab.subgroup),
  
  "GTT (Adj)" = lm(out_diab_screen_gtt_12 ~ biweekly_counter + period_COVID + period_FFCRA +
                       biweekly_counter*period_COVID + biweekly_counter*period_FFCRA +  
                       age + no_transfusion_weight,
                     data = diab.subgroup)
)

# Create combined table with star notation for p-values
tbl_merge(
  tbls = lapply(models_list, function(x) {
    tbl_regression(x,
                  intercept = TRUE,
                  estimate_fun = ~ style_number(.x, digits = 3),
                  conf.int = FALSE,
                  pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
      add_significance_stars(hide_p = TRUE, 
                           pattern = "{estimate}{stars}") %>% 
      modify_column_hide(std.error)
  }),
  tab_spanner = names(models_list)
) %>% 
  as_flex_table() %>% 
  FitFlextableToPage()
```

{{< pagebreak >}}

# Supplemental

```{r}
library(DiagrammeR)
library(DiagrammeRsvg)
library(webshot)
library(dplyr)

# Updated cohort with me_code filter
final_cohort <- episodes %>%
  filter(age >= 19 & age <= 55,
         enrolled_birth == 1,
         state_tx == "TX",
         los <= 60,
         me_code == "R")

# Count cohort steps
n0 <- nrow(episodes)
n1 <- episodes %>% filter(age >= 19 & age <= 55) %>% nrow()
n2 <- episodes %>% filter(age >= 19 & age <= 55, enrolled_birth == 1) %>% nrow()
n3 <- episodes %>% filter(age >= 19 & age <= 55, enrolled_birth == 1, state_tx == "TX") %>% nrow()
n4 <- episodes %>% filter(age >= 19 & age <= 55, enrolled_birth == 1, state_tx == "TX", los <= 60) %>% nrow()
n5 <- nrow(final_cohort)
n5_diab <- final_cohort %>% filter(diab_sample == 1) %>% nrow()
n5_htn  <- final_cohort %>% filter(htn_sample == 1) %>% nrow()

# Create and export the updated diagram
svg_code <- export_svg(
  grViz(sprintf("
    digraph cohort_flow {
      graph [layout = dot, rankdir = TB]
      node [shape = box, style = filled, fillcolor = LightGray, fontname = Helvetica, width = 3]

      A [label = 'Initial episodes\\n(n = %d)']
      B [label = 'Aged 19-55\\n(n = %d)']
      C [label = 'Enrolled at birth\\n(n = %d)']
      D [label = 'Texas residents\\n(n = %d)']
      E [label = 'LOS <= 60 days\\n(n = %d)']
      F [label = 'ME_CODE = R\\n(n = %d)']
      G [label = 'Diabetes sample\\n(n = %d)']
      H [label = 'Hypertension sample\\n(n = %d)']

      A -> B -> C -> D -> E -> F
      F -> G
      F -> H
    }
  ", n0, n1, n2, n3, n4, n5, n5_diab, n5_htn))
)

# Save the SVG to file
writeLines(svg_code, "flowchart.svg")

# Convert the SVG to PNG
webshot::webshot("flowchart.svg", file = "flowchart.png", vwidth = 1000, vheight = 900)
```
